---
title: 'Review Analysis Tests: Review Length Test for Cables with Overvall Stats'
author: "Eugenie"
date: "11/11/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Data pre-processing is included, where special chars and minimal stop-words are removed.
```{r echo=T, results='hide', message=F, warning=F}
library(data.table)
## load review data
source("~/Dropbox/Eugenie/scripts/libs.R")
```

```{r, include=FALSE}
# Load review data
reviews3.csv <- read.csv("~/Dropbox/Eugenie/data/processed/merged-reviews.csv")
reviews3.csv$date <- as.Date(reviews3.csv$date, "%Y-%m-%d")
# Load new AmazonBasics cable data
merged_cables <- read.csv("~/Dropbox/Eugenie/data/processed/merged-cables.csv")
# Load brand data
cable_brands <- read_excel("~/Dropbox/Eugenie/data/raw/amazon-cables.xlsx")
```


# Data Processing

```{r}
# Combine the cable datasets
#reviews3.cables <- reviews3.csv[, !names(reviews3.csv) %in% c("sentiment_cat", "positive", "negative", "neutral", "mixed")]
#reviews3.csv <- rbind(reviews3.csv, amazon_cables)
```

```{r, include=FALSE}
# Drop records before 2013.
reviews3.csv <- reviews3.csv[as.numeric(as.character(reviews3.csv$year))>2013,]
# Drop records with no product category.
reviews3.csv <- reviews3.csv[reviews3.csv$product_cat != 'none',]
# Get selected columns for further analysis.
reviews.product <- reviews3.csv[,c('recid','item_id','child_id', 'incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week')]
```

```{r, include=FALSE}
# Add 'after_ban' label
reviews.product['after_ban'] <- ifelse(reviews.product$date>'2016-10-02',1,0)
reviews.product$after_ban <- as.factor(reviews.product$after_ban)
levels(reviews.product$after_ban) <- c("before", "after")
```

# Analyse Amazon Products
```{r, include=FALSE}
# Get cables
cables <- reviews.product[reviews.product$product_cat == "phone_cables",]
# Get brands
cables <- merge(cables, cable_brands, by='item_id', all.x=T)
cables2 <- cables[is.na(cables$brand),]
# Get brands for child_id
cables2 <- merge(cables2, cable_brands, by.x = 'child_id', by.y = 'item_id')
cables <- na.omit(cables)
# Merge
#colnames(cables2)[46] <- "brand"
#cables2 <- cables2[,names(cables)]
cables2 <- cables2[,c('recid','item_id','child_id', 'incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week','after_ban','brand.y')]
names(cables2) <- c('recid','item_id','child_id', 'incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week','after_ban','brand')
cables <- rbind(cables, cables2)
```

```{r, include=FALSE}
cables["brand.sim"] <- ifelse(cables$brand %in% c('AmazonBasics'), "AmazonBasics", 
                              ifelse(cables$brand %in% c('Anker'), "Anker", 
                                     ifelse(cables$brand %in% c('RAMPOW'), "RAMPOW", "other")))
#merged_cables["Amazon"] <- ifelse(merged_cables$brand == "AmazonBasics", 1, 0)
#merged_cables["Anker"] <- ifelse(merged_cables$brand == "Anker", 1, 0)
#merged_cables["RAMPOW"] <- ifelse(merged_cables$brand == "RAMPOW", 1, 0)
#merged_cables["other"] <- ifelse(!merged_cables$brand %in% c("AmazonBasics", "RAMPOW", "Anker"), 1, 0)
#write.csv(reviews.product, file = "processed-cables.csv",row.names=FALSE)
```

## Percentage of incentivized reviews
```{r,echo=FALSE}
## get the percentage of each group
cable.summary <- data.frame(table(cables[,c('incentivized')]))
cable.summary <- ddply(cable.summary, .(), mutate, Freq_pct = Freq/sum(Freq)*100)
knitr::kable(cable.summary)
```

```{r,echo=FALSE}
## get the percentage of each group
cable.summary <- data.frame(table(cables[,c('incentivized','brand.sim')]))
cable.summary <- ddply(cable.summary, .(brand.sim), mutate, Freq_pct = Freq/sum(Freq)*100)
knitr::kable(cable.summary)
```

```{r,echo=FALSE}
## get the percentage of each group
cable.summary <- data.frame(table(cables[,c('incentivized','brand.sim','after_ban')]))
cable.summary <- ddply(cable.summary, .(after_ban), mutate, Freq_pct = Freq/sum(Freq)*100)

## cast for readibility
knitr::kable(cast(cable.summary, incentivized~brand.sim~after_ban, mean, value = 'Freq'))
```

```{r, include=FALSE}
reviews.product <- cables
```

# Analysis Test: Average Review Length
Once we have the word count distribution of the product and the expected distribution of the category we compare the two distributions and identify product word count groups that are higher in concentration than we’d expect to see.

## Data Processing

Get mean, variance, and standard deviation of the number of reviews per day by item.
```{r, include=FALSE}
reviews.length <- reviews.product[reviews.product$after_ban == "before",] %>%
  #group_by(brand.sim) %>%
  mutate(sd = sd(word_count)) %>%
  mutate(variance = var(word_count)) %>%
  mutate(mean = mean(word_count))

#reviews.length <- reviews.length[,c('brand.sim', "sd", "variance", "mean")] %>% distinct()
reviews.length <- reviews.length[,c("sd", "variance", "mean")] %>% distinct()
```

Compute stds
```{r,echo=FALSE}
reviews.length <- reviews.length %>%
  #group_by(brand.sim) %>%
  mutate(threshold_2sd = mean+2*sd) %>%
  mutate(threshold_3sd = mean+3*sd)
```

Label pass/fail tests
```{r,echo=FALSE}
#reviews.product <- merge(reviews.product, reviews.length, by = 'brand.sim')
reviews.product <- merge(reviews.product, reviews.length)
reviews.product['word_count.2sd'] <- ifelse(reviews.product$word_count>reviews.product$threshold_2sd, 'fail', 'pass')
reviews.product['word_count.3sd'] <- ifelse(reviews.product$word_count>reviews.product$threshold_3sd, 'fail', 'pass')
```


## Result Analysis

### Two standard deviations away

```{r,echo=FALSE}
temp <- data.frame(table(reviews.product[,c('brand.sim','after_ban','word_count.2sd')]))
temp<-temp[!(temp$brand.sim=="none"),]
temp$word_count.2sd <- paste0(temp$after_ban,'_',temp$word_count.2sd)
temp <- temp[,c('brand.sim','word_count.2sd','Freq')]
#knitr::kable(ddply(temp, .(word_count.2sd), mutate, Freq_pct = Freq/sum(Freq)*100))
```

```{r,echo=FALSE}
table.length <- reshape(temp, idvar = "brand.sim", timevar = c('word_count.2sd'), direction = "wide")

temp <- reviews.length[,c('mean','variance','sd','threshold_2sd')] %>% distinct()

table.length <- table.length %>%
  group_by(brand.sim) %>%
  mutate(Before.fail.pct = Freq.before_fail/(Freq.before_pass+Freq.before_fail)*100) %>%
  mutate(After.fail.pct = Freq.after_fail/(Freq.after_pass+Freq.after_fail)*100)

table.length <- merge(table.length, temp)
knitr::kable(table.length)
```

Mean review rating for over vs. under length threshold for the number of reviews.

```{r,echo=FALSE}
product.avg <- aggregate(reviews.product[, 'rating'], list(reviews.product$brand.sim,reviews.product$word_count.2sd), mean)
names(product.avg) <- c('brand.sim','reviews.count','avg.rating')
product.avg <- reshape(product.avg, idvar = 'brand.sim',timevar = 'reviews.count', direction = 'wide')
knitr::kable(product.avg)
```

Review distribution between groups.
```{r,echo=FALSE}
ggplot(data=reviews.product, aes(word_count.2sd))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  scale_fill_brewer(palette="RdBu", name='rating')+
  facet_grid(~brand.sim)+
  ylab('proportion')
```


### Three standard deviations away
```{r,echo=FALSE}
temp <- data.frame(table(reviews.product[,c('brand.sim','after_ban','word_count.3sd')]))
temp<-temp[!(temp$brand.sim=="none"),]
temp$word_count.3sd <- paste0(temp$after_ban,'_',temp$word_count.3sd)
temp <- temp[,c('brand.sim','word_count.3sd','Freq')]
#knitr::kable(ddply(temp, .(word_count.3sd), mutate, Freq_pct = Freq/sum(Freq)*100))
```

```{r,echo=FALSE}
table.length <- reshape(temp, idvar = "brand.sim", timevar = c('word_count.3sd'), direction = "wide")

temp <- reviews.product[,c('brand.sim','mean','variance','sd','threshold_3sd')] %>% distinct()

table.length <- table.length %>%
  group_by(brand.sim) %>%
  mutate(Before.fail.pct = Freq.before_fail/(Freq.before_pass+Freq.before_fail)*100) %>%
  mutate(After.fail.pct = Freq.after_fail/(Freq.after_pass+Freq.after_fail)*100)

table.length <- merge(table.length, temp, by = 'brand.sim')
knitr::kable(table.length)
```

Mean review rating for over vs. under length threshold for the number of reviews.

```{r,echo=FALSE}
product.avg <- aggregate(reviews.product[, 'rating'], list(reviews.product$brand.sim,reviews.product$word_count.3sd), mean)
names(product.avg) <- c('brand.sim','reviews.count','avg.rating')
product.avg <- reshape(product.avg, idvar = 'brand.sim',timevar = 'reviews.count', direction = 'wide')
knitr::kable(product.avg)
```

Review distribution between groups.

```{r,echo=FALSE}
ggplot(data=reviews.product, aes(word_count.3sd))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  scale_fill_brewer(palette="RdBu", name='rating')+
  facet_grid(~brand.sim)+
  ylab('proportion')
```

