---
title: "AmazonBasics Product Categories & Review Date/Time Part 2"
author: "Eugenie"
date: "02/11/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Data pre-processing is included, where special chars and minimal stop-words are removed.
```{r echo=T, results='hide', message=F, warning=F}
library(data.table)
## load review data
source("~/Dropbox/Eugenie/scripts/libs.R")
```

```{r, include=FALSE}
# Load review data
reviews.csv <- read.csv("~/Dropbox/Eugenie/data/processed_reviewMeta/merged-reviews.csv")
reviews.csv$date <- as.Date(reviews.csv$date, "%Y-%m-%d")
reviews.csv$week <- as.Date(reviews.csv$week, "%Y-%m-%d")
# Load brand data
cable_brands <- read_excel("~/Dropbox/Eugenie/data/ReviewMeta_Amazon_Data/amazon-cables.xlsx")
```

# Data Processing

```{r, include=FALSE}
# Drop records before 2013.
reviews.csv <- reviews.csv[as.numeric(as.character(reviews.csv$year))>2013,]
# Drop records with no product category.
reviews.csv <- reviews.csv[reviews.csv$product_cat != 'none',]
# Get selected columns for further analysis.
reviews.product <- reviews.csv[,c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week')]
```

```{r, include=FALSE}
# Add 'after_ban' label
reviews.product['after_ban'] <- ifelse(reviews.product$date>'2016-10-02',1,0)
reviews.product$after_ban <- as.factor(reviews.product$after_ban)
levels(reviews.product$after_ban) <- c("before", "after")
```

# Analyse Amazon Products
```{r, include=FALSE}
# Get cables
cables <- reviews.product[reviews.product$product_cat == "phone_cables",]
# Get brands
cables <- merge(cables, cable_brands, by='item_id', all.x=T)
cables2 <- cables[is.na(cables$brand),]
# Get brands for child_id
cables2 <- merge(cables2, cable_brands, by.x = 'child_id', by.y = 'item_id')
cables <- na.omit(cables)
# Merge
cables2 <- cables2[,c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week','after_ban','brand.y')]
names(cables2) <- c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week','after_ban','brand')
cables <- rbind(cables, cables2)
```

```{r, include=FALSE}
cables["brand.sim"] <- ifelse(cables$brand %in% c('AmazonBasics'), "AmazonBasics", 
                              ifelse(cables$brand %in% c('Anker'), "Anker", 
                                     ifelse(cables$brand %in% c('RAMPOW'), "RAMPOW", "other")))
```

```{r,include=FALSE}
# Compute rating stats without splitting incentivized vs. non-incentivized reviews at all
reviews.product <- cables

# Mean rating by day
reviews.product <- reviews.product %>%
  group_by(brand.sim, date) %>%
  mutate(day_rating = mean(rating))

# Mean rating by week
reviews.product <- reviews.product %>%
  group_by(brand.sim, year, week) %>%
  mutate(week_rating = mean(rating))

# Mean word_count by day
reviews.product <- reviews.product %>%
  group_by(brand.sim, date) %>%
  mutate(day_length = mean(word_count))

# Mean word_count by week
reviews.product <- reviews.product %>%
  group_by(brand.sim, year, week) %>%
  mutate(week_length = mean(word_count))
```

```{r,include=FALSE}
# Bin the review length
bins <- c(-1,10,20,30,50,100,200,Inf)
reviews.product['word_count.binned'] <- cut(reviews.product$word_count, breaks=bins,
                                        labels=c('0-10','10-20','20-30','30-50','50-100','100-200','200+'))
reviews.product$word_count.binned <- as.factor(reviews.product$word_count.binned)
```

```{r, include=FALSE}
# For the review length test: 
# Get mean, variance, and standard deviation of the number of reviews per day by item
reviews.length <- reviews.product[reviews.product$after_ban == "before",] %>%
  group_by(brand.sim) %>%
  mutate(sd = sd(word_count)) %>%
  mutate(variance = var(word_count)) %>%
  mutate(mean = mean(word_count))

reviews.length <- reviews.length[,c("brand.sim", "sd", "variance", "mean")] %>% distinct()
```

```{r,echo=FALSE}
# Compute stds
reviews.length <- reviews.length %>%
  group_by(brand.sim) %>%
  mutate(threshold_2sd = mean+2*sd) %>%
  mutate(threshold_3sd = mean+3*sd)
```

```{r,echo=FALSE}
# Label pass/fail tests
reviews.product <- merge(reviews.product, reviews.length, by = 'brand.sim')
reviews.product['word_count.2sd'] <- ifelse(reviews.product$word_count>reviews.product$threshold_2sd, 'fail', 'pass')
reviews.product['word_count.3sd'] <- ifelse(reviews.product$word_count>reviews.product$threshold_3sd, 'fail', 'pass')
```


# Time Data vs. Rating

## Plot mean rating over time by brand.sim without splitting incentivized vs. non-incentivized reviews at all

### Rating average by day
```{r}
## Plot by day
ggplot(NULL, aes(x = date, y = day_rating))+
  geom_point(data=reviews.product, aes(color = "daily ave rating"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='daily ave rating line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')
```

### Rating averaged by week
```{r,echo=FALSE}
## Plot by week
ggplot(NULL, aes(x = week, y = week_rating))+
  geom_point(data=reviews.product, aes(color = "weekly ave rating"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='weekly ave rating line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

## Plot rating distribution by proportion

### Rating proportion in a day
```{r,echo=FALSE}
## Percentage of rating vs. week
ggplot(data=reviews.product, aes(date))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

### Rating proportion in a week
```{r,echo=FALSE}
## Percentage of rating vs. week
ggplot(data=reviews.product, aes(week))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```


# Time Data vs. Review Length

## Average review length
### Length average by day
```{r}
## Plot by day
ggplot(NULL, aes(x = date, y = day_length))+
  geom_point(data=reviews.product, aes(color = "daily ave length"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='daily ave length line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean length',fill='category',title='Product Category Mean Length by Day')
```

### Length averaged by week
```{r,echo=FALSE}
## Plot by week
ggplot(NULL, aes(x = week, y = week_length))+
  geom_point(data=reviews.product, aes(color = "weekly ave length"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='weekly ave length line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean length',fill='category',title='Product Category Mean Length by Week')
```


## Plot rating distribution by proportion
### Rating proportion in a day
```{r,echo=FALSE}
ggplot(data=reviews.product, aes(date))+
  geom_bar(aes(fill=word_count.binned), position="fill")+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

### Rating proportion in a week
```{r,echo=FALSE}
## Percentage of rating vs. week
ggplot(data=reviews.product, aes(week))+
  geom_bar(aes(fill=word_count.binned), position="fill")+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

# Passing vs. Failing Reviews
```{r,include=FALSE}
# Compute stats grouped by 2sd results
# Mean rating by day
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.2sd, date) %>%
  mutate(day_rating.2sd = mean(rating))

# Mean rating by week
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.2sd, year, week) %>%
  mutate(week_rating.2sd = mean(rating))

# Mean word_count by day
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.2sd, date) %>%
  mutate(day_length.2sd = mean(word_count))

# Mean word_count by week
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.2sd, year, week) %>%
  mutate(week_length.2sd = mean(word_count))
```

```{r,include=FALSE}
# Compute stats grouped by 3sd results
# Mean rating by day
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.3sd, date) %>%
  mutate(day_rating.3sd = mean(rating))

# Mean rating by week
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.3sd, year, week) %>%
  mutate(week_rating.3sd = mean(rating))

# Mean word_count by day
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.3sd, date) %>%
  mutate(day_length.3sd = mean(word_count))

# Mean word_count by week
reviews.product <- reviews.product %>%
  group_by(brand.sim, word_count.3sd, year, week) %>%
  mutate(week_length.3sd = mean(word_count))
```

```{r,include=FALSE}
## Split on test result
pass.2sd <- reviews.product[reviews.product$word_count.2sd=='pass',]
fail.2sd <- reviews.product[reviews.product$word_count.2sd=='fail',]
pass.3sd <- reviews.product[reviews.product$word_count.3sd=='pass',]
fail.3sd <- reviews.product[reviews.product$word_count.3sd=='fail',]
```

## Rating average by day
### 2sd
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_rating.2sd))+
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.3,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')
```

### 3sd
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_rating.3sd))+
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.3,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')
```

## Rating averaged by week
### 2sd
```{r,echo=FALSE}
## by week
ggplot(NULL, aes(x = week, y = week_rating.2sd))+ 
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.7,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

### 3sd
```{r,echo=FALSE}
## by week
ggplot(NULL, aes(x = week, y = week_rating.3sd))+ 
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.7,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

## Length average by day
### 2sd
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_length.2sd))+
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.3,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')
```

### 3sd
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_length.3sd))+
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.3,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')
```

## Length averaged by week
### 2sd
```{r,echo=FALSE}
## by week
ggplot(NULL, aes(x = week, y = week_length.2sd))+ 
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.7,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

### 3sd
```{r,echo=FALSE}
## by week
ggplot(NULL, aes(x = week, y = week_length.3sd))+ 
  geom_point(data=pass.2sd, aes(color = "passing"), alpha = 0.7,size=0.2)+
  geom_point(data=fail.2sd, aes(color = "failing"), alpha = 0.7,size=0.2)+
  geom_smooth(data=pass.2sd,method = 'auto',aes(color='passing-line'),size=1,alpha = 0.6)+
  geom_smooth(data=fail.2sd,method = 'auto',aes(color='failing-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.sim))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

