---
title: "AWS Sentiment & Review Date/Time Part 2"
author: "Eugenie"
date: "07/08/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Data pre-processing is included, where special chars and minimal stop-words are removed.
```{r echo=T, results='hide', message=F, warning=F}
## load review data
source("~/Dropbox/Eugenie/scripts/utils.R")
```

Load AWS review sentiment data.
```{r}
#aws_reviews <- read.csv("~/Dropbox/Eugenie/data/processed/sentiment/aws-reviews2-all.csv")
reviews3.csv <- read.csv("~/Dropbox/Eugenie/data/processed/processed-reviews3.csv")
```


# Data Processing
Add category data as extra columns. Join on either item_id or child_id.
```{r}
#reviews2.temp <- reviews2.csv

reviews.product <- reviews3.csv[,c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','weeks','positive','neutral')]

names(reviews.product) <- c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week','positive','neutral')

reviews.product$date <- as.Date(reviews.product$date, "%Y-%m-%d")
reviews.product <- reviews.product[reviews.product$product_cat != 'none',]
```

Drop records before 2012.
```{r}
#reviews2.temp <- reviews2.temp[as.numeric(as.character(reviews2.temp$year))>2013,]
```

Drop records after 2018-10-07 since it's not a full week.
```{r}
#reviews2.temp <- reviews2.temp[reviews2.temp$date < '2018-10-07',]
```

Drop records with no product category.
```{r}
#reviews2.temp <- reviews2.temp[reviews2.temp$product_cat != 'none',]
```

Get selected columns for further analysis.
```{r}
#reviews.product <- merge(aws_reviews,reviews2.temp[,c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week')])
```

Compute positive sentiment stats without splitting incentivized vs. non-incentivized reviews at all.
```{r,include=FALSE}
## mean positive sentiment probability by day
reviews.product <- reviews.product %>%
  group_by(product_cat, date) %>%
  mutate(day_positive = mean(positive))

## mean positive sentiment probability by week
# reviews.product <- reviews.product %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_positive = mean(positive))
# 
# ## mean positive sentiment probability by month
# reviews.product <- reviews.product %>%
#   group_by(product_cat, month) %>%
#   mutate(month_positive = mean(positive))
```

Compute negative sentiment stats without splitting incentivized vs. non-incentivized reviews at all.
```{r,include=FALSE}
## mean negative sentiment probability by day
reviews.product <- reviews.product %>%
  group_by(product_cat, date) %>%
  mutate(day_negative = mean(negative))

## mean negative sentiment probability by week
# reviews.product <- reviews.product %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_negative = mean(negative))
# 
# ## mean negative sentiment probability by month
# reviews.product <- reviews.product %>%
#   group_by(product_cat, month) %>%
#   mutate(month_negative = mean(negative))
```

Compute mixed sentiment stats without splitting incentivized vs. non-incentivized reviews at all.
```{r,include=FALSE}
## mean mixed sentiment probability by day
reviews.product <- reviews.product %>%
  group_by(product_cat, date) %>%
  mutate(day_mixed = mean(mixed))

## mean mixed sentiment probability by week
# reviews.product <- reviews.product %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_mixed = mean(mixed))
# 
# ## mean mixed sentiment probability by month
# reviews.product <- reviews.product %>%
#   group_by(product_cat, month) %>%
#   mutate(month_mixed = mean(mixed))
```

Compute neutral sentiment stats without splitting incentivized vs. non-incentivized reviews at all.
```{r,include=FALSE}
## mean neutral sentiment probability by day
reviews.product <- reviews.product %>%
  group_by(product_cat, date) %>%
  mutate(day_neutral = mean(neutral))

## mean neutral sentiment probability by week
# reviews.product <- reviews.product %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_neutral = mean(neutral))
# 
# ## mean neutral sentiment probability by month
# reviews.product <- reviews.product %>%
#   group_by(product_cat, month) %>%
#   mutate(month_neutral = mean(neutral))
```

Bin the probability of positive to five bins.
```{r}
bins <- c(-1,0.2,0.4,0.6,0.8,Inf)
reviews.product['positive.binned'] <- cut(reviews.product$positive, 
                                        breaks=bins, labels=c('<20%','20-40%','40-60%','60-80%','>80%'))
reviews.product$positive.binned <- as.factor(reviews.product$positive.binned)
```

Bin the probability of negative to five bins.
```{r,include=FALSE}
bins <- c(-1,0.2,0.4,0.6,0.8,Inf)
reviews.product['negative.binned'] <- cut(reviews.product$negative, 
                                        breaks=bins, labels=c('<20%','20-40%','40-60%','60-80%','>80%'))
reviews.product$negative.binned <- as.factor(reviews.product$negative.binned)
```

Bin the probability of mixed to five bins.
```{r,include=FALSE}
bins <- c(-1,0.2,0.4,0.6,0.8,Inf)
reviews.product['mixed.binned'] <- cut(reviews.product$mixed, 
                                        breaks=bins, labels=c('<20%','20-40%','40-60%','60-80%','>80%'))
reviews.product$mixed.binned <- as.factor(reviews.product$mixed.binned)
```

Bin the probability of neutral to five bins.
```{r,include=FALSE}
bins <- c(-1,0.2,0.4,0.6,0.8,Inf)
reviews.product['neutral.binned'] <- cut(reviews.product$neutral, 
                                        breaks=bins, labels=c('<20%','20-40%','40-60%','60-80%','>80%'))
reviews.product$neutral.binned <- as.factor(reviews.product$neutral.binned)
```


# Time Data vs. Positive Sentiment Probability

## Plot mean positive sentiment probability over time by product_cat without splitting incentivized vs. non-incentivized reviews at all

### Positive sentiment probability average by day
```{r}
## plot by day
ggplot(NULL, aes(x = date, y = day_positive))+
  geom_point(data=reviews.product, aes(color = "daily ave positive"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='daily ave positive line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean positive',fill='category',title='Product Category Mean positive by Day')
```

### Positive sentiment probability averaged by week
```{r,echo=FALSE}
## plot by week
# ggplot(NULL, aes(x = week, y = week_positive))+
#   geom_point(data=reviews.product, aes(color = "weekly ave positive"), alpha = 0.7,size=0.2)+
#   geom_smooth(data=reviews.product,method = 'auto',aes(color='weekly ave positive line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   labs(x='day',y='mean positive',fill='category',title='Product Category Mean positive by Week')
```

### Positive sentiment probability averaged by month
```{r,echo=FALSE}
## plot by month
# ggplot(NULL, aes(x = month, y = month_positive))+
#   geom_point(data=reviews.product, aes(color = "monthly ave positive"), alpha = 0.7,size=0.2)+
#   geom_smooth(data=reviews.product,method = 'auto',aes(color='monthly ave positive line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   labs(x='day',y='mean positive',fill='category',title='Product Category Mean positive by Month')
```


## Plot positive sentiment probability distribution by proportion

### Positive sentiment probability proportion in a day
```{r,echo=FALSE}
ggplot(data=reviews.product, aes(date))+
  geom_bar(aes(fill=positive.binned), position="fill")+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

### Positive sentiment probability proportion in a week
```{r,echo=FALSE}
## percentage of positive sentiment probability vs. week
# ggplot(data=reviews.product, aes(week))+
#   geom_bar(aes(fill=positive.binned), position="fill")+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   scale_fill_brewer(palette="RdBu")+
#   ylab('proportion')
```

### Positive sentiment probability proportion in a month
```{r,echo=FALSE}
# ggplot(data=reviews.product, aes(month))+
#   geom_bar(aes(fill=positive.binned), position="fill")+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   scale_fill_brewer(palette="RdBu")+
#   ylab('proportion')
```


## Plot positive sentiment probability distribution by count

### Positive sentiment probability count in a day
```{r,echo=FALSE}
ggplot(reviews.product, aes(date, fill=positive.binned))+
  geom_bar()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")
```

### Positive sentiment probability count in a week
```{r,echo=FALSE}
# ggplot(reviews.product, aes(week, fill=positive.binned))+
#   geom_bar()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   scale_fill_brewer(palette="RdBu")
```

### Positive sentiment probability count in a month
```{r,echo=FALSE}
# ggplot(reviews.product, aes(month, fill=positive.binned))+
#   geom_bar()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   scale_fill_brewer(palette="RdBu")
```


# Time Data vs. Neutral Sentiment Probability

## Plot mean neutral sentiment probability over time by product_cat without splitting incentivized vs. non-incentivized reviews at all

### Neutral sentiment probability average by day
```{r}
## plot by day
ggplot(NULL, aes(x = date, y = day_neutral))+
  geom_point(data=reviews.product, aes(color = "daily ave neutral"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='daily ave neutral line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean neutral',fill='category',title='Product Category Mean neutral by Day')
```

### Neutral sentiment probability averaged by week
```{r,echo=FALSE}
## plot by week
# ggplot(NULL, aes(x = week, y = week_neutral))+
#   geom_point(data=reviews.product, aes(color = "weekly ave neutral"), alpha = 0.7,size=0.2)+
#   geom_smooth(data=reviews.product,method = 'auto',aes(color='weekly ave neutral line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   labs(x='day',y='mean neutral',fill='category',title='Product Category Mean neutral by Week')
```

### Neutral sentiment probability averaged by month
```{r,echo=FALSE}
## plot by month
# ggplot(NULL, aes(x = month, y = month_neutral))+
#   geom_point(data=reviews.product, aes(color = "monthly ave neutral"), alpha = 0.7,size=0.2)+
#   geom_smooth(data=reviews.product,method = 'auto',aes(color='monthly ave neutral line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   labs(x='day',y='mean neutral',fill='category',title='Product Category Mean neutral by Month')
```





