---
title: "AWS Sentiment & Review Date/Time Part 1"
author: "Eugenie"
date: "07/08/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Load data.
```{r, include=FALSE}
########################## load library ############################
## for data manipulation
library(plyr)
library(dplyr)
library(tidyr)
library(purrr)
library(readr)
library(stringr)
library(reshape)

## for plotting
library(ggplot2)
library(ggmosaic)
library(plotly)
library(ggpubr)

## for modelling
library(plm)
library(mgcv)
library(GoodmanKruskal)

## for sentiment analysis
library(tidytext)
library(textdata)
library(textclean)
library(gutenbergr)
library(scales)
library(tm)
library(sentimentr)

## read .xlsx files
library(readxl)

## time/date
library(chron)
library(lubridate)

## for tables
library(stargazer)

reviews3.csv <- read.csv("~/Dropbox/Eugenie/data/processed/processed-reviews3.csv")
```


# Data Processing
Get selected columns for further analysis.
```{r}
reviews.product <- reviews3.csv[,c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','weeks','positive','neutral')]

names(reviews.product) <- c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week','positive','neutral')
```

Drop records before 2012.
```{r}
#reviews2.temp <- reviews2.temp[as.numeric(as.character(reviews2.temp$year))>2013,]
```

Drop records after 2018-10-07 since it's not a full week.
```{r}
## turn factor to date variable
reviews.product$date <- as.Date(reviews.product$date, "%Y-%m-%d")
#reviews2.temp <- reviews2.temp[reviews2.temp$date < '2019-09-16',]
```

Drop records with no product category.
```{r}
reviews.product <- reviews.product[reviews.product$product_cat != 'none',]
```


# Time Data vs. Positive Sentiment Probability
## Data processing

Split data on date without splitting incentivized vs. non-incentivized reviews after 2016-10-03.
```{r,include=FALSE}
## split on date
reviews.product_non <- reviews.product[reviews.product$date<'2016-10-03'&reviews.product$incentivized=='non-incentivized',]
reviews.product_incentivized <- reviews.product[reviews.product$date<'2016-10-03'&reviews.product$incentivized=='incentivized',]
reviews.product_after <- reviews.product[reviews.product$date>'2016-10-03',]
```

Compute positive sentiment stats without splitting incentivized vs. non-incentivized reviews after 2016-10-03.
```{r,include=FALSE}
## mean positive sentiment probability by day
reviews.product_non <- reviews.product_non %>%
  group_by(product_cat, date) %>%
  mutate(day_positive = mean(positive))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(product_cat, date) %>%
  mutate(day_positive = mean(positive))

reviews.product_after <- reviews.product_after %>%
  group_by(product_cat, date) %>%
  mutate(day_positive = mean(positive))

## mean positive sentiment probability by week
# reviews.product_non <- reviews.product_non %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_positive = mean(positive))
# 
# reviews.product_incentivized <- reviews.product_incentivized %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_positive = mean(positive))
# 
# reviews.product_after <- reviews.product_after %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_positive = mean(positive))

# ## mean positive sentiment probability by month
# reviews.product_non <- reviews.product_non %>%
#   group_by(product_cat, month) %>%
#   mutate(month_positive = mean(positive))
# 
# reviews.product_incentivized <- reviews.product_incentivized %>%
#   group_by(product_cat, month) %>%
#   mutate(month_positive = mean(positive))
# 
# reviews.product_after <- reviews.product_after %>%
#   group_by(product_cat, month) %>%
#   mutate(month_positive = mean(positive))
```

## Plot mean positive sentiment probability over time by product_cat without splitting incentivized vs. non-incentivized reviews after 2016-10-03

### Positive sentiment probability average by day
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_positive))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.3,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean positive sentiment probability',fill='category',title='Product Category Mean Positive Sentiment Probability by Day')
```

Observed that prior to 2016-10-03, the day average of incentivized reviews is generally higher and has a greater variation than non-incentivized reviews.

### Positive sentiment probability averaged by week
```{r,echo=FALSE}
# ## by week
# ggplot(NULL, aes(x = week, y = week_positive))+ 
#   geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 0.7,size=0.2)+
#   geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.7,size=0.2)+
#   geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.7,size=0.2)+
#   geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   labs(x='week',y='mean positive sentiment probability',fill='category',title='Product Category Mean Positive Sentiment Probability by Week')
```

### Positive sentiment probability averaged by month
```{r,echo=FALSE}
# ## by month
# ggplot(NULL, aes(x = month, y = month_positive, color = product_cat))+
#   geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
#   geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
#   geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.5,size=0.2)+
#   geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-02'), color = "black", size=0.3)+
#   labs(x='month',y='mean positive sentiment probability',fill='category',title='Product Category Mean Positive Sentiment Probability by Month')

```


# Time Data vs. Neutral Sentiment Probability
## Data processing

Compute neutral sentiment stats without splitting incentivized vs. non-incentivized reviews after 2016-10-03.
```{r,include=FALSE}
## mean neutral sentiment probability by day
reviews.product_non <- reviews.product_non %>%
  group_by(product_cat, date) %>%
  mutate(day_neutral = mean(neutral))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(product_cat, date) %>%
  mutate(day_neutral = mean(neutral))

reviews.product_after <- reviews.product_after %>%
  group_by(product_cat, date) %>%
  mutate(day_neutral = mean(neutral))

## mean neutral sentiment probability by week
# reviews.product_non <- reviews.product_non %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_neutral = mean(neutral))
# 
# reviews.product_incentivized <- reviews.product_incentivized %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_neutral = mean(neutral))
# 
# reviews.product_after <- reviews.product_after %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_neutral = mean(neutral))
# 
# ## mean neutral sentiment probability by month
# reviews.product_non <- reviews.product_non %>%
#   group_by(product_cat, month) %>%
#   mutate(month_neutral = mean(neutral))
# 
# reviews.product_incentivized <- reviews.product_incentivized %>%
#   group_by(product_cat, month) %>%
#   mutate(month_neutral = mean(neutral))
# 
# reviews.product_after <- reviews.product_after %>%
#   group_by(product_cat, month) %>%
#   mutate(month_neutral = mean(neutral))
```


## Plot mean neutral sentiment probability over time by product_cat without splitting incentivized vs. non-incentivized reviews after 2016-10-03

### Neutral sentiment probability average by day
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_neutral))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.3,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean neutral sentiment probability',fill='category',title='Product Category Mean Neutral Sentiment Probability by Day')
```

Observed that prior to 2016-10-03, the day average of incentivized reviews is generally higher and has a greater variation than non-incentivized reviews.

### Neutral sentiment probability averaged by week
```{r,echo=FALSE}
## by week
# ggplot(NULL, aes(x = week, y = week_neutral))+ 
#   geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 0.7,size=0.2)+
#   geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.7,size=0.2)+
#   geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.7,size=0.2)+
#   geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
#   labs(x='week',y='mean neutral sentiment probability',fill='category',title='Product Category Mean Neutral Sentiment Probability by Week')
```

### Neutral sentiment probability averaged by month
```{r,echo=FALSE}
## by month
# ggplot(NULL, aes(x = month, y = month_neutral, color = product_cat))+
#   geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
#   geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
#   geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.5,size=0.2)+
#   geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
#   geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
#   theme_minimal()+
#   facet_grid(rows=vars(product_cat))+
#   geom_vline(xintercept = as.Date('2016-10-02'), color = "black", size=0.3)+
#   labs(x='month',y='mean neutral sentiment probability',fill='category',title='Product Category Mean Neutral Sentiment Probability by Month')

```
