---
title: "Exploratory Analysis on Review Length, Number of Helpful Yes's, and Images Included"
author: "Eugenie"
date: "14/07/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
## for data manipulation
library(plyr)
library(dplyr)
library(reshape)

## for plotting
library(ggplot2)
library(ggmosaic)
library(plotly)
library(ggpubr)

## for modelling
library(plm)
library(mgcv)
library(GoodmanKruskal)
```


# Data Processing
Load data. Please check the file path.
```{r}
reviews2.csv <- read.csv('~/Dropbox/Eugenie/data/raw/arslan-reviews2.csv')
```

Turn numeric values to factors.
```{r}
## turn numeric values to factors
reviews2.csv$is_deleted <- as.factor(reviews2.csv$is_deleted)
reviews2.csv$incentivized <- as.factor(reviews2.csv$incentivized)
reviews2.csv$verified_purchaser <- as.factor(reviews2.csv$verified_purchaser)

## change level values
levels(reviews2.csv$verified_purchaser) <- c("unverified", "verified")
levels(reviews2.csv$incentivized) <- c("non-incentivized", "incentivized")
levels(reviews2.csv$is_deleted) <- c("kept", "deleted")
```

Turn factors to numeric
```{r}
reviews2.csv$helpful_total <- as.numeric(as.character(reviews2.csv$helpful_total))
reviews2.csv$helpful_yes <- as.numeric(as.character(reviews2.csv$helpful_yes))
reviews2.csv$image_count <- as.numeric(as.character(reviews2.csv$image_count))
#reviews2.csv$video <- as.numeric(as.character(reviews2.csv$video))
```



# Review Length Exploratory Analysis
## Plots
### Plot incentivized vs. non-incentivized reviews

```{r, echo=FALSE}
## plot incentivized vs. non-incentivized reviews
p1 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'incentivized',], aes(x=word_count))+
  geom_histogram(binwidth = 50)+
  labs(x='incentivized')
p0 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'non-incentivized',], aes(x=word_count))+ 
  geom_histogram(binwidth = 50)+
  labs(x='non-incentivized')

subplot(
  ggplotly(p0),
  ggplotly(p1),
  nrows = 1, margin = 0.005,
  titleX = TRUE
)
```


### Review length distribution by group
Get the mean of incentivized vs. non-incentivized reviews
```{r}
aggregate(reviews2.csv[, 'word_count'], list(reviews2.csv$incentivized), mean)
```

Get the mean of is_deleted vs. non-deleted reviews
```{r}
aggregate(reviews2.csv[, 'word_count'], list(reviews2.csv$is_deleted), mean)
```

Get the mean of verified_purchaser vs. non-verified_purchaser reviews
```{r}
aggregate(reviews2.csv[, 'word_count'], list(reviews2.csv$verified_purchaser), mean)
```

Bin review length by 50 for further analysis
```{r}
## binning length
bins <- c(-1,50,100,150,200,250,500,Inf)
reviews2.csv.binned <- reviews2.csv[,c('recid','item_id','rating','helpful_yes','helpful_total',
                                       'image_count','word_count','brand_repeat',
                                       'incentivized','is_deleted','verified_purchaser')]
reviews2.csv.binned$word_count <- cut(reviews2.csv.binned$word_count, breaks=bins, labels=c('0-50','50-100','100-150','150-200','200-250','250-500','500+'))

```

```{r, echo=FALSE}
## plot percentage distribution: incentivized

p1 <- ggplot(data=reviews2.csv.binned, aes(incentivized))+
  geom_bar(aes(fill=as.factor(word_count)), position="fill")+
  scale_fill_brewer(palette="RdBu")

p1 <- ggplotly(p1)

## plot percentage distribution: is_deleted
p2 <- ggplot(data=reviews2.csv.binned, aes(is_deleted))+
  geom_bar(aes(fill=as.factor(word_count)), position="fill")+
  scale_fill_brewer(palette="RdBu")

p2 <- ggplotly(p2)

## plot percentage distribution: verified_purchaser
p3 <- ggplot(data=reviews2.csv.binned, aes(verified_purchaser))+
  geom_bar(aes(fill=as.factor(word_count)), position="fill")+
  scale_fill_brewer(palette="RdBu")

p3 <- ggplotly(p3)

subplot(
  style(p1, showlegend = FALSE),
  style(p2, showlegend = FALSE),
  p3, 
  nrows = 1, margin = 0.005,
  shareY = TRUE, titleX = TRUE
)
```


## Models and Tests on Review Length
### Formula
```{r}
formula.fe <- word_count ~ incentivized + is_deleted + verified_purchaser
```

### linear fixed effect model for review2.csv on review length
```{r}
# in model.fe, index = c('item_id') defines 'item_id' as the entity
model.fe <- plm(data = reviews2.csv, formula = formula.fe, index = c('item_id'), model = 'within')
# get the model summary
summary(model.fe)
```
From the result of the linear fixed effect modelling, the null hypothesis of the independency of products is rejected. 




# Review Number of Helpful Yes and Total Exploratory Analysis
## Plots
### Summary stats
```{r}
summary(reviews2.csv$helpful_total)
```

```{r}
summary(reviews2.csv$helpful_yes)
```
Over 80% of the reviews have a NULL number of helpful_total and helpful_yes.

```{r}
summary(reviews2.csv$helpful_total-reviews2.csv$helpful_yes)
```
Observe negative numbers where the number of helpful_total is smaller than the number of helpful_yes. Not sure how this happened. For the simplicity of the further analysis, we'll only focus on the number of helpful_yes for now.

```{r}
table(reviews2.csv[is.na(reviews2.csv$helpful_yes),c('incentivized')])
```
Not sure how the NA's are generated but a large number of NA's are from non-incentivized reviews.

### Plot of the number of helpful yes of incentivized vs. non-incentivized reviews
NA's are not included, so it only plots < 20% of the reviews
```{r, echo=FALSE}
## plot incentivized vs. non-incentivized reviews
p1 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'incentivized',], aes(x=helpful_yes))+
  geom_histogram(binwidth = 5)+
  labs(x='incentivized')
p0 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'non-incentivized',], aes(x=helpful_yes))+ 
  geom_histogram(binwidth = 5)+
  labs(x='non-incentivized')

subplot(
  ggplotly(p0),
  ggplotly(p1),
  nrows = 1, margin = 0.005,
  titleX = TRUE
)
```

### Plot of the number of helpful total of incentivized vs. non-incentivized reviews
NA's are not included, so it only plots < 20% of the reviews
```{r, echo=FALSE}
## plot incentivized vs. non-incentivized reviews
p1 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'incentivized',], aes(x=helpful_total))+
  geom_histogram(binwidth = 5)+
  labs(x='incentivized')
p0 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'non-incentivized',], aes(x=helpful_total))+ 
  geom_histogram(binwidth = 5)+
  labs(x='non-incentivized')

subplot(
  ggplotly(p0),
  ggplotly(p1),
  nrows = 1, margin = 0.005,
  titleX = TRUE
)
```

### Number of helpful_yes distribution by group
Reviews with NA number of helpful_yes are omitted.

Get the mean of incentivized vs. non-incentivized reviews
```{r}
aggregate(reviews2.csv[!is.na(reviews2.csv$helpful_yes), 'helpful_yes'], list(reviews2.csv[!is.na(reviews2.csv$helpful_yes),]$incentivized), mean)
```

Get the mean of is_deleted vs. non-deleted reviews
```{r}
aggregate(reviews2.csv[!is.na(reviews2.csv$helpful_yes), 'helpful_yes'], list(reviews2.csv[!is.na(reviews2.csv$helpful_yes),]$is_deleted), mean)
```

Get the mean of verified_purchaser vs. non-verified_purchaser reviews
```{r}
aggregate(reviews2.csv[!is.na(reviews2.csv$helpful_yes), 'helpful_yes'], list(reviews2.csv[!is.na(reviews2.csv$helpful_yes),]$verified_purchaser), mean)
```

Bin number of helpful_yes by 5 for further analysis
```{r}
## binning length
bins <- c(-1,5,10,Inf)
reviews2.csv.binned$helpful_yes <- cut(reviews2.csv.binned$helpful_yes, breaks=bins, labels=c('0-5','5-10','10+'))

```

```{r, echo=FALSE}
## plot percentage distribution: incentivized

p1 <- ggplot(data=reviews2.csv.binned, aes(incentivized))+
  geom_bar(aes(fill=as.factor(helpful_yes)), position="fill")+
  scale_fill_discrete(na.value='white')

p1 <- ggplotly(p1)

## plot percentage distribution: is_deleted
p2 <- ggplot(data=reviews2.csv.binned, aes(is_deleted))+
  geom_bar(aes(fill=as.factor(helpful_yes)), position="fill")+
  scale_fill_discrete(na.value='white')

p2 <- ggplotly(p2)

## plot percentage distribution: verified_purchaser
p3 <- ggplot(data=reviews2.csv.binned, aes(verified_purchaser))+
  geom_bar(aes(fill=as.factor(helpful_yes)), position="fill")+
  scale_fill_discrete(na.value='white')

p3 <- ggplotly(p3)

subplot(
  style(p1, showlegend = FALSE),
  style(p2, showlegend = FALSE),
  p3, 
  nrows = 1, margin = 0.005,
  shareY = TRUE, titleX = TRUE
)
```

It's interesting to see there're more helpful yes counts in the incentivized reviews vs. non-incentivized.

## Models and Tests on Number of helpful_yes
### Formula
```{r}
formula.fe <- helpful_yes ~ incentivized + is_deleted + verified_purchaser
```

### linear fixed effect model for review2.csv on number of helpful_yes without setting NA's to 0
```{r}
# in model.fe, index = c('item_id') defines 'item_id' as the entity
model.fe <- plm(data = reviews2.csv, formula = formula.fe, index = c('item_id'), model = 'within')
# get the model summary
summary(model.fe)
```
 

### linear fixed effect model for review2.csv on number of helpful_yes with setting NA's to 0
```{r}
data <- reviews2.csv[,c('item_id','helpful_yes','incentivized','is_deleted','verified_purchaser')]
data[is.na(data)] <- 0
# in model.fe, index = c('item_id') defines 'item_id' as the entity
model.fe <- plm(data = data, formula = formula.fe, index = c('item_id'), model = 'within')
# get the model summary
summary(model.fe)
```
From the result of the linear fixed effect modelling, the null hypothesis of the independency of products is rejected. 

It's surprising to me that setting all NA's to zeros would make such a difference. 


# Review Number of Image Included Exploratory Analysis
## Plots
### Summary stats
```{r}
summary(reviews2.csv$image_count)
```

Over 80% of the reviews have a NULL number of image_count.

```{r}
image_count.summary <- data.frame(table(reviews2.csv[is.na(reviews2.csv$image_count),c('incentivized')]))
image_count.summary <- ddply(image_count.summary, .(), mutate, Freq_pct = Freq/sum(Freq)*100)
image_count.summary[,2:ncol(image_count.summary)]
```
Not sure how the NA's are generated but a large number of NA's are from non-incentivized reviews.

### Plot of the number of helpful yes of incentivized vs. non-incentivized reviews
NA's are not included, so it only plots < 20% of the reviews
```{r, echo=FALSE}
## plot incentivized vs. non-incentivized reviews
p1 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'incentivized',], aes(x=image_count))+
  geom_histogram(binwidth = 5)+
  labs(x='incentivized')
p0 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'non-incentivized',], aes(x=image_count))+ 
  geom_histogram(binwidth = 5)+
  labs(x='non-incentivized')

subplot(
  ggplotly(p0),
  ggplotly(p1),
  nrows = 1, margin = 0.005,
  titleX = TRUE
)
```


### Number of image_count distribution by group
Reviews with NA number of image_count are omitted.

Get the mean of incentivized vs. non-incentivized reviews
```{r}
aggregate(reviews2.csv[!is.na(reviews2.csv$image_count), 'image_count'], list(reviews2.csv[!is.na(reviews2.csv$image_count),]$incentivized), mean)
```

Get the mean of is_deleted vs. non-deleted reviews
```{r}
aggregate(reviews2.csv[!is.na(reviews2.csv$image_count), 'image_count'], list(reviews2.csv[!is.na(reviews2.csv$image_count),]$is_deleted), mean)
```

Get the mean of verified_purchaser vs. non-verified_purchaser reviews
```{r}
aggregate(reviews2.csv[!is.na(reviews2.csv$image_count), 'image_count'], list(reviews2.csv[!is.na(reviews2.csv$image_count),]$verified_purchaser), mean)
```

Bin number of image_count by 5 for further analysis
```{r}
## binning length
bins <- c(-1,5,10,Inf)
reviews2.csv.binned$image_count <- cut(reviews2.csv.binned$image_count, breaks=bins, labels=c('0-5','5-10','10+'))

```

```{r, echo=FALSE}
## plot percentage distribution: incentivized

p1 <- ggplot(data=reviews2.csv.binned, aes(incentivized))+
  geom_bar(aes(fill=as.factor(image_count)), position="fill")+
  scale_fill_discrete(na.value='white')

p1 <- ggplotly(p1)

## plot percentage distribution: is_deleted
p2 <- ggplot(data=reviews2.csv.binned, aes(is_deleted))+
  geom_bar(aes(fill=as.factor(image_count)), position="fill")+
  scale_fill_discrete(na.value='white')

p2 <- ggplotly(p2)

## plot percentage distribution: verified_purchaser
p3 <- ggplot(data=reviews2.csv.binned, aes(verified_purchaser))+
  geom_bar(aes(fill=as.factor(image_count)), position="fill")+
  scale_fill_discrete(na.value='white')

p3 <- ggplotly(p3)

subplot(
  style(p1, showlegend = FALSE),
  style(p2, showlegend = FALSE),
  p3, 
  nrows = 1, margin = 0.005,
  shareY = TRUE, titleX = TRUE
)
```

It's interesting to see there're more image counts in the incentivized reviews vs. non-incentivized.

## Models and Tests on Number of image_count
### Formula
```{r}
formula.fe <- image_count ~ incentivized + is_deleted + verified_purchaser
```

### linear fixed effect model for review2.csv on number of image_count without setting NA's to 0
```{r}
# in model.fe, index = c('item_id') defines 'item_id' as the entity
model.fe <- plm(data = reviews2.csv, formula = formula.fe, index = c('item_id'), model = 'within')
# get the model summary
summary(model.fe)
```
 

### linear fixed effect model for review2.csv on number of image_count with setting NA's to 0
```{r}
data <- reviews2.csv[,c('item_id','image_count','incentivized','is_deleted','verified_purchaser')]
data[is.na(data)] <- 0
# in model.fe, index = c('item_id') defines 'item_id' as the entity
model.fe <- plm(data = data, formula = formula.fe, index = c('item_id'), model = 'within')
# get the model summary
summary(model.fe)
```

The difference is not as big as the fixed effect linear model of the helpful_yes even when all NA's are set to zeros.



