---
title: "Data Exploration and Plots"
author: "Eugenie"
date: "02/07/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
## for data manipulation
library(plyr)
library(dplyr)
library(reshape)

## for plotting
library(ggplot2)
library(ggmosaic)
library(plotly)
library(ggpubr)

## for modelling
library(plm)
library(mgcv)
library(GoodmanKruskal)
```


# Plots
Load data. Please check the file path.
```{r}
reviews2.csv <- read.csv('~/Dropbox/Eugenie/data/arslan-reviews2.csv')
```

Turn numeric values to factors.
```{r}
## turn numeric values to factors
reviews2.csv$is_deleted <- as.factor(reviews2.csv$is_deleted)
reviews2.csv$incentivized <- as.factor(reviews2.csv$incentivized)
reviews2.csv$verified_purchaser <- as.factor(reviews2.csv$verified_purchaser)

## change level values
levels(reviews2.csv$verified_purchaser) <- c("unverified", "verified")
levels(reviews2.csv$incentivized) <- c("non-incentivized", "incentivized")
levels(reviews2.csv$is_deleted) <- c("kept", "deleted")
```


## Plot incentivized vs. non-incentivized reviews

```{r, echo=FALSE}
## plot incentivized vs. non-incentivized reviews
p1 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'incentivized',], aes(x=rating))+ 
  geom_bar()+
  geom_text(stat='count', aes(label=..count..), vjust=-1)+
  labs(x='incentivized')
p0 <- ggplot(reviews2.csv[reviews2.csv$incentivized == 'non-incentivized',], aes(x=rating))+ 
  geom_bar()+
  geom_text(stat='count', aes(label=..count..), vjust=-1)+
  labs(x='non-incentivized')

subplot(
  ggplotly(p0),
  ggplotly(p1),
  nrows = 1, margin = 0.005,
  titleX = TRUE
)
```


## Rating distribution by group
Get the mean of incentivized vs. non-incentivized reviews
```{r}
aggregate(reviews2.csv[, 'rating'], list(reviews2.csv$incentivized), mean)
```

Get the mean of is_deleted vs. non-deleted reviews
```{r}
aggregate(reviews2.csv[, 'rating'], list(reviews2.csv$is_deleted), mean)
```

Get the mean of verified_purchaser vs. non-verified_purchaser reviews
```{r}
aggregate(reviews2.csv[, 'rating'], list(reviews2.csv$verified_purchaser), mean)
```

```{r, echo=FALSE}
## plot percentage distribution: incentivized

p1 <- ggplot(data=reviews2.csv, aes(incentivized))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  scale_fill_brewer(palette="RdBu")

p1 <- ggplotly(p1)

## plot percentage distribution: is_deleted
p2 <- ggplot(data=reviews2.csv, aes(is_deleted))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  scale_fill_brewer(palette="RdBu")

p2 <- ggplotly(p2)

## plot percentage distribution: verified_purchaser
p3 <- ggplot(data=reviews2.csv, aes(verified_purchaser))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  scale_fill_brewer(palette="RdBu")

p3 <- ggplotly(p3)

subplot(
  style(p1, showlegend = FALSE),
  style(p2, showlegend = FALSE),
  p3, 
  nrows = 1, margin = 0.005,
  shareY = TRUE, titleX = TRUE
)
```

## Group distribution
### Group distribution stats
#### Stats sub-grouped by verified reviews
Counts sub-grouped by verified reviews.
```{r, echo=FALSE}
table(reviews2.csv[,c('incentivized', 'is_deleted', 'verified_purchaser')])
```

Percentage sub-grouped by verified reviews.
```{r, echo=FALSE}
## get the percentage of each group
reviews2.summary <- data.frame(table(reviews2.csv[,c('incentivized', 'is_deleted', 'verified_purchaser')]))
reviews2.summary <- ddply(reviews2.summary, .(verified_purchaser), mutate, Freq_pct = Freq/sum(Freq)*100)

## cast for readibility
cast(reviews2.summary, incentivized~is_deleted~verified_purchaser, mean, value = 'Freq_pct')
```
It's interesting that:

- A much higher percentage of incentivized reviews are made by unverified purchasers compared to verified (looking at the bottom row of the two tables)

- If you are a verified purchaser, your non-incentivized reviews are more likely to be kept (94.051% vs. 79.637%)

- A higher percentage of non-incentivized reviews from unverified purchasers (11.051%) are deleted than those from verified purchasers (5.852%)

- A higher percentage of incentivized reviews from unverified purchasers (1.016%) are kept than those from verified purchasers (0.035%)

The following stats (sub-grouped by the other two review categories and distribution by every combination of the groups) are for verifying the findings.

#### Stats sub-grouped by deleted reviews
Percentage sub-grouped by is_deleted
```{r, echo=FALSE}
## get the percentage of each group
reviews2.summary <- data.frame(table(reviews2.csv[,c('verified_purchaser', 'incentivized', 'is_deleted')]))
reviews2.summary <- ddply(reviews2.summary, .(is_deleted), mutate, Freq_pct = Freq/sum(Freq)*100)

## cast for readibility
cast(reviews2.summary, verified_purchaser~incentivized~is_deleted, mean, value = 'Freq_pct')
```

#### Stats sub-grouped by incentivized reviews
Percentage sub-grouped by incentivized
```{r, echo=FALSE}
## get the percentage of each group
reviews2.summary <- data.frame(table(reviews2.csv[,c('verified_purchaser', 'is_deleted', 'incentivized')]))
reviews2.summary <- ddply(reviews2.summary, .(incentivized), mutate, Freq_pct = Freq/sum(Freq)*100)

## cast for readibility
cast(reviews2.summary, verified_purchaser~is_deleted~incentivized, mean, value = 'Freq_pct')
```

#### Percentage of each group
```{r, echo=FALSE}
## get the percentage of each group
reviews2.summary <- data.frame(table(reviews2.csv[,c('verified_purchaser', 'is_deleted', 'incentivized')]))
reviews2.summary <- ddply(reviews2.summary, .(), mutate, Freq_pct = Freq/sum(Freq)*100)

## show selected columns
reviews2.summary[,c('incentivized', 'is_deleted', 'verified_purchaser', 'Freq', 'Freq_pct')]
```


### Plots for group distribution
#### Mosaic plots to visualize all three categories
Plot three groups together with a mosaic plot with facets on verified reviews
```{r, echo=FALSE}
ggplotly(ggplot(data = reviews2.csv) +
  geom_mosaic(aes(x = product(incentivized, is_deleted), fill=incentivized), na.rm=TRUE)+
  facet_grid(verified_purchaser~.)+
  labs(x='is deleted?'))
```

Plot three groups together with a mosaic plot
```{r, echo=FALSE}
ggplotly(ggplot(data = reviews2.csv) +
  geom_mosaic(aes(x = product(verified_purchaser, is_deleted), fill=incentivized), na.rm=TRUE)+
  labs(x='incentivized:is_deleted'))
```


#### Bar charts to visualize the combination of any two categories
Plot the proportion of deleted reviews in non-/incentivized group
```{r, echo=FALSE}
ggplotly(ggplot(data=reviews2.csv, aes(incentivized))+
  geom_bar(aes(fill=is_deleted), position="fill"))
```


Plot the proportion of verified reviews in non-/incentivized group
```{r, echo=FALSE}
ggplotly(ggplot(data=reviews2.csv, aes(incentivized))+
  geom_bar(aes(fill=verified_purchaser), position="fill"))
```


Plot the proportion of verified reviews in non-/deleted group
```{r, echo=FALSE}
ggplotly(ggplot(data=reviews2.csv, aes(is_deleted))+
  geom_bar(aes(fill=verified_purchaser), position="fill"))
```


## Group Correlation
### Chi-square tests on pairs of the three groups
Incentivized vs. is_deleted
```{r}
chisq.test(reviews2.csv$incentivized, reviews2.csv$is_deleted, correct = FALSE)
```

Incentivized vs. verified_purchaser
```{r}
chisq.test(reviews2.csv$incentivized, reviews2.csv$verified_purchaser, correct = FALSE)
```

Is_deleted vs. verified_purchaser
```{r}
chisq.test(reviews2.csv$is_deleted, reviews2.csv$verified_purchaser, correct = FALSE)
```

From the tests above, there correlation between the pairs are significant. Is there a way to find out the correlation between three categorical variables?

### Effect size
Goodman and Kruskal's tau to calculate the effect size (strength of association). Although the results of chi-square tests suggest the significance of the association between the groups, the effect size result shows they are not good predictors of one another.
```{r}
reviews2.temp <- reviews2.csv[,c('incentivized', 'is_deleted', 'verified_purchaser')]
GKmatrix1<- GKtauDataframe(reviews2.temp)
plot(GKmatrix1, corrColors = "blue")
```


# Models and Tests
## Formula
```{r}
formula.fe <- rating ~ incentivized + is_deleted + verified_purchaser
```

## linear fixed effect model for review2.csv
```{r}
# in model.fe, index = c('item_id') defines 'item_id' as the entity
model.fe <- plm(data = reviews2.csv, formula = formula.fe, index = c('item_id'), model = 'within')
# get the model summary
summary(model.fe)
```
From the result of the linear fixed effect modelling, the null hypothesis of the independency of products is rejected. 
