---
title: "Create the diff-in-diff dataset from ReviewMeta dataset"
author: "Eugenie Lai"
date: "25/03/2020"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Data pre-processing is included, where special chars and minimal stop-words are removed.
```{r echo=T, results='hide', message=F, warning=F}
library(data.table)
library(coefplot)
library("arm")
## load review data
source("~/Dropbox/Eugenie/scripts/libs.R")
```

- Load review data and brand data
```{r, include=FALSE}
# Load review data
reviews.csv <- read.csv("~/Dropbox/Eugenie/data/processed_reviewMeta/merged-reviews.csv")
reviews.csv$date <- as.Date(reviews.csv$date, "%Y-%m-%d")
reviews.csv$week <- as.Date(reviews.csv$week, "%Y-%m-%d")
```

- Get reviews 6 months before and after the ban
```{r, include=FALSE}
# Get reviews 6 months before and after the ban
reviews.csv <- reviews.csv[reviews.csv$date>'2016-04-02',]
reviews.csv <- reviews.csv[reviews.csv$date<'2017-04-02',]
```


```{r, include=FALSE}
# Load brand data
cable_brands <- read_excel("~/Dropbox/Eugenie/data/ReviewMeta_Amazon_Data/amazon-cables.xlsx")
tablet_brands <- read_excel("~/Dropbox/Eugenie/data/ReviewMeta_Amazon_Data/amazon-tablets.xlsx")
```


# Data Processing

- Drop records with no product category
```{r, include=FALSE}
# Drop records with no product category.
reviews.csv <- reviews.csv[reviews.csv$product_cat != 'none',]
# Get selected columns for further analysis.
reviews.product <- reviews.csv[,c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week')]
```

- Add 'after_ban' label
```{r, include=FALSE}
# Add 'after_ban' label
reviews.product['after_ban'] <- ifelse(reviews.product$date>'2016-10-02',1,0)
#reviews.product$after_ban <- as.factor(reviews.product$after_ban)
#levels(reviews.product$after_ban) <- c("before", "after")
```

# Get Amazon and non-Non-Amazon products from cable and tablet category
```{r, include=FALSE}
# Get cables
cables <- reviews.product[reviews.product$product_cat == "phone_cables",]
# Get brands
cables <- merge(cables, cable_brands, by='item_id', all.x=T)
cables2 <- cables[is.na(cables$brand),]
# Get brands for child_id
cables2 <- merge(cables2, cable_brands, by.x = 'child_id', by.y = 'item_id')
cables <- na.omit(cables)
# Merge
cables2 <- cables2[,c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week','after_ban','brand.y')]
names(cables2) <- c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week','after_ban','brand')
cables <- rbind(cables, cables2)
```

```{r, include=FALSE}
# Get tablets
tablets <- reviews.product[reviews.product$product_cat == "tablets",]
# Get brands
tablets <- merge(tablets, tablet_brands, by='item_id', all.x=T)
tablets2 <- tablets[is.na(tablets$brand),]
# Get brands for child_id
tablets2 <- merge(tablets2, cable_brands, by.x = 'child_id', by.y = 'item_id')
tablets <- na.omit(tablets)
# Merge
tablets2 <- tablets2[,c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week','after_ban','brand.y')]
names(tablets2) <- c('recid','item_id','child_id','product_cat', 'incentivized','verified_purchaser','positive','rating','word_count','helpful_yes','image_count','date','year','month','week','after_ban','brand')
tablets <- rbind(tablets, tablets2)
```

```{r, include=FALSE}
# Merge cables and tablets
did.reviews <- rbind(cables, tablets)
```


# Get weekly measurements
```{r, include=FALSE}
# Convert labels from factor to numeric
levels(did.reviews$incentivized) <- c(1, 0)
levels(did.reviews$verified_purchaser) <- c(0, 1)
did.reviews$incentivized <- as.numeric(as.character(did.reviews$incentivized))
did.reviews$verified_purchaser <- as.numeric(as.character(did.reviews$verified_purchaser))
```

```{r, include=FALSE}
# List of dependent variables
# Compute weekly stats for each product
# Mean measurement by week
did.reviews <- did.reviews %>%
  group_by(item_id, week) %>%
  mutate(week_n = n()) %>%
  mutate(week_rating = mean(rating)) %>%
  mutate(week_positive = mean(positive)) %>%
  mutate(week_word_count = mean(word_count)) %>%
  mutate(week_helpful_yes = mean(helpful_yes)) %>%
  mutate(week_image_count = mean(image_count))
```

```{r, include=FALSE}
did.reviews <- did.reviews %>%
  group_by(item_id, week) %>%
  mutate(week_n_incentivized = sum(incentivized)) %>%
  mutate(week_n_verified = sum(verified_purchaser)) %>%
  mutate(week_incentivized = week_n_incentivized / week_n) %>%
  mutate(week_verified = week_n_verified / week_n)
```

```{r, results='asis', echo=FALSE}
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ word_count + image_count, index = c('product_cat'), model = 'within')

stargazer(fe.helpful_yes, title="Linear Regression FE on Product Category Results", align=TRUE, type='html', dep.var.labels=c("Helpfulness"), covariate.labels=c("Length","Image count"))
```

```{r, results='asis', echo=FALSE}
fe.rating <- plm(data = did.reviews, formula = rating ~ incentivized, index = c('product_cat'), model = 'within')
fe.positive <- plm(data = did.reviews, formula = positive ~ incentivized, index = c('product_cat'), model = 'within')
fe.word_count <- plm(data = did.reviews, formula = word_count ~ incentivized, index = c('product_cat'), model = 'within')
fe.image <- plm(data = did.reviews, formula = image_count ~ incentivized, index = c('product_cat'), model = 'within')
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ incentivized, index = c('product_cat'), model = 'within')

stargazer(fe.rating, fe.positive, fe.word_count, fe.helpful_yes, fe.image, title="Linear Regression FE on Product Category Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness","Image count"), covariate.labels=c("Incentivized"))
```

```{r, results='asis', echo=FALSE}
fe.rating <- plm(data = did.reviews, formula = rating ~ incentivized, index = c('brand'), model = 'within')
fe.positive <- plm(data = did.reviews, formula = positive ~ incentivized, index = c('brand'), model = 'within')
fe.word_count <- plm(data = did.reviews, formula = word_count ~ incentivized, index = c('brand'), model = 'within')
fe.image <- plm(data = did.reviews, formula = image_count ~ incentivized, index = c('brand'), model = 'within')
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ incentivized, index = c('brand'), model = 'within')

stargazer(fe.rating, fe.positive, fe.word_count, fe.helpful_yes, fe.image, title="Linear Regression FE on Brand Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness","Image count"), covariate.labels=c("Incentivized"))
```

```{r, results='asis', echo=FALSE}
fe.rating <- plm(data = did.reviews, formula = rating ~ incentivized, index = c('item_id'), model = 'within')
fe.positive <- plm(data = did.reviews, formula = positive ~ incentivized, index = c('item_id'), model = 'within')
fe.word_count <- plm(data = did.reviews, formula = word_count ~ incentivized, index = c('item_id'), model = 'within')
fe.image <- plm(data = did.reviews, formula = image_count ~ incentivized, index = c('item_id'), model = 'within')
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ incentivized, index = c('item_id'), model = 'within')

stargazer(fe.rating, fe.positive, fe.word_count, fe.helpful_yes, fe.image, title="Linear Regression FE on Product Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness","Image count"), covariate.labels=c("Incentivized"))
```


# Get products
```{r, include=FALSE}
did.products <- did.reviews[,c('item_id','child_id','product_cat','week_n','week_positive','week_rating','week_word_count','week_helpful_yes','week_image_count','week_incentivized','week_verified','year','month','week','after_ban','brand')]
did.products <- did.products %>% distinct()
```

```{r, include=FALSE}
# Add amazon attribute
did.products['non_amazon_product'] <- ifelse(did.products$brand %in% c('AmazonBasics','fire'), 0, 1)
```

```{r, include=FALSE}
# Write to save
#write.csv(did.reviews, file="did_reviews_reviewMeta.csv", row.names=FALSE)
```

```{r, include=FALSE}
# Split to Amazon and non-Non-Amazon products
did.amazon <- did.products[did.products$non_amazon_product == 0,]
did.nonamazon <- did.products[did.products$non_amazon_product == 1,]
```

```{r}
library(knitr)
library(kableExtra)
table <- did.products %>% 
  group_by(product_cat) %>% 
  summarize(brand_count = n_distinct(brand),
            product_count = n_distinct(item_id))
names(table) <- c('Product Category','Brand Count','Product Count')
table %>%
  kable() %>%
  kable_styling()
```

# Diff-in-diff Estimator

```{r, results='asis', echo=FALSE}
# Estimating the DID estimator
didreg.rating = lm(week_rating ~ non_amazon_product * after_ban, data = did.products)
didreg.sentiment = lm(week_positive ~ non_amazon_product * after_ban, data = did.products)
didreg.length = lm(week_word_count ~ non_amazon_product * after_ban, data = did.products)
didreg.helpfulness = lm(week_helpful_yes ~ non_amazon_product * after_ban, data = did.products)
didreg.image = lm(week_image_count ~ non_amazon_product * after_ban, data = did.products)

stargazer(didreg.rating, didreg.sentiment, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness", "Image count"),covariate.labels=c("Non-Amazon product","After ban","Non-Amazon product x After ban","Constant"), add.lines=list(c("Product Category Fixed Effects",rep("No", 5)),c("Brand Fixed Effects",rep("No", 5))))
```

```{r, results='asis', echo=FALSE}
# Estimating the DID estimator
pdf <- pdata.frame(did.products, index = c("product_cat"))
didreg.rating = plm(week_rating ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.sentiment = plm(week_positive ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.length = plm(week_word_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.helpfulness = plm(week_helpful_yes ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.image = plm(week_image_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")

stargazer(didreg.rating, didreg.sentiment, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference with FE on Product Category Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness", "Image count"),covariate.labels=c("Non-Amazon product","After ban","Non-Amazon product x After ban","Constant"),
add.lines=list(c("Product Category Fixed Effects",rep("Yes", 5)),c("Brand Fixed Effects",rep("No", 5))))
```

```{r results='asis', echo=FALSE}
# {r eval = FALSE, results='asis', echo=FALSE}
# Estimating the DID estimator
pdf <- pdata.frame(did.products, index = c("brand"))
didreg.rating = plm(week_rating ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.sentiment = plm(week_positive ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.length = plm(week_word_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.helpfulness = plm(week_helpful_yes ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.image = plm(week_image_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")

stargazer(didreg.rating, didreg.sentiment, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference with FE on Brand Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness", "Image count"),covariate.labels=c("After ban","Non-Amazon product x After ban"), add.lines=list(c("Product Category Fixed Effects",rep("No", 5)),c("Brand Fixed Effects",rep("Yes", 5))))
```


```{r eval = FALSE, results='asis', echo=FALSE}
# {r eval = FALSE, results='asis', echo=FALSE}
# Estimating the DID estimator
pdf <- pdata.frame(did.products, index = c("item_id"))
didreg.rating = plm(week_rating ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.sentiment = plm(week_positive ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.length = plm(week_word_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.helpfulness = plm(week_helpful_yes ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.image = plm(week_image_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")

stargazer(didreg.rating, didreg.sentiment, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference with FE on Product Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness", "Image count"),covariate.labels=c("After ban","Non-Amazon product x After ban"))
```

# Testing the Assumptions

```{r, results='asis', echo=FALSE}
did.before <- did.products[did.products$after_ban == 0,]
did.before$month <- as.factor(did.before$month)
didreg.rating.before <- lm(week_rating ~ non_amazon_product * month, data = did.before)
didreg.sentiment.before <- lm(week_positive ~ non_amazon_product * month, data = did.before)
didreg.length.before <- lm(week_word_count ~ non_amazon_product * month, data = did.before)
didreg.helpfulness.before <- lm(week_helpful_yes ~ non_amazon_product * month, data = did.before)
didreg.image.before <- lm(week_image_count ~ non_amazon_product * month, data = did.before)

#stargazer(didreg.rating.before, didreg.sentiment.before, didreg.length.before, didreg.helpfulness.before, didreg.image.before, title="Difference-in-Difference Pre-Treatment Parallel Assumption Check", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness", "Image count"))
```

```{r}
new_names = c('Intercept', 'NA','2016 May','2016 June','2016 July','2016 Aug','2016 Sept','2016 Oct','NA x May', 'NA x June', 'NA x July', 'NA x Aug', 'NA x Sept', 'NA x Oct')
new_names2 = c('Intercept', 'Non-Amazon','2016 May','2016 June','2016 July','2016 Aug','2016 Sept','2016 Oct','Non-Amazon x May', 'Non-Amazon x June', 'Non-Amazon x July', 'Non-Amazon x Aug', 'Non-Amazon x Sept', 'Non-Amazon x Oct')
names(didreg.rating.before[["coefficients"]]) <- new_names2
names(didreg.sentiment.before[["coefficients"]]) <- new_names2
names(didreg.length.before[["coefficients"]]) <- new_names2
names(didreg.helpfulness.before[["coefficients"]]) <- new_names2
names(didreg.image.before[["coefficients"]]) <- new_names2
coef_cols = names(didreg.rating.before[["coefficients"]])[9:14]
#new_names = c('NA x 2016 May', 'NA x 2016 June', 'Non-Amazon x 2016 July', 'Non-Amazon x 2016 August', 'Non-Amazon x 2016 September', 'Non-Amazon x 2016 October')
empty_names = c("","","","","","","","","","","","","","")
```

```{r}
library(fixest)
```

```{r}
fixest::coefplot(didreg.rating.before, main = '', col='blue', horiz=TRUE, drop=c('Intercept','2016'))
fixest::coefplot(didreg.sentiment.before, x.shift = .3, add = TRUE, col="red", horiz=TRUE)
#fixest::coefplot(didreg.length.before, x.shift = .2, add = TRUE, col="darkgreen", horiz=TRUE)
fixest::coefplot(didreg.helpfulness.before, x.shift = 0.6, add = TRUE, col="darkorange", horiz=TRUE)
fixest::coefplot(didreg.image.before, x.shift = 0.9, add = TRUE, col="black", horiz=TRUE)
legend("topright", col = c('blue','red','darkorange','black'), pch = 16, lwd = 1,
       legend = c("Rating", "Sentiment",'Helpfulness','Image Count'), title = "Standard-Errors")
```

```{r}
fixest::coefplot(didreg.length.before, col="darkgreen", horiz=TRUE, drop=c('Intercept','2016'))
legend("topright", col = c('darkgreen'), pch = 16, lwd = 1,
       legend = c("Word Count"), title = "Standard-Errors")
```


```{r}
coefplot(didreg.length.before, col.pts="darkgreen", intercept=TRUE, varnames = new_names, main = 'Word Count', var.las=2)
```

```{r}
coefplot(didreg.rating.before, col.pts="black", intercept=TRUE, varnames = new_names, main = 'Rating and Sentiment', )
coefplot(didreg.sentiment.before, add=TRUE, col.pts="red", intercept=TRUE, varnames = new_names)
```

```{r}
coefplot(didreg.helpfulness.before, col.pts="darkorange", intercept=TRUE, varnames = new_names, main = 'Helpfuness and Image Count', )
coefplot(didreg.image.before, add=TRUE, col.pts="blue", intercept=TRUE, varnames = new_names)
```


```{r, results='asis', echo=FALSE}
did.before <- did.products[did.products$after_ban == 1,]
did.before$month <- as.factor(did.before$month)
didreg.rating.before <- lm(week_rating ~ non_amazon_product * month, data = did.before)
didreg.sentiment.before <- lm(week_positive ~ non_amazon_product * month, data = did.before)
didreg.length.before <- lm(week_word_count ~ non_amazon_product * month, data = did.before)
didreg.helpfulness.before <- lm(week_helpful_yes ~ non_amazon_product * month, data = did.before)
didreg.image.before <- lm(week_image_count ~ non_amazon_product * month, data = did.before)

stargazer(didreg.rating.before, didreg.sentiment.before, didreg.length.before, didreg.helpfulness.before, didreg.image.before, title="Difference-in-Difference Post-Treatment Check", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness", "Image count"))
```

