---
title: "Create the diff-in-diff dataset from ReviewMeta dataset"
author: "Eugenie Lai"
date: "25/03/2020"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Data pre-processing is included, where special chars and minimal stop-words are removed.
```{r echo=T, results='hide', message=F, warning=F}
library(data.table)
## load review data
source("~/Dropbox/Eugenie/scripts/libs.R")
```

- Load review data and brand data
```{r, include=FALSE}
# Load review data
reviews <- read.csv("~/Dropbox/Eugenie/data/processed_julian_amazon_data/did/reviews_mcauley_description_full.csv")
```

- Get reviews 6 months before and after the ban
```{r, eval = FALSE, include=FALSE}
# Get reviews 6 months before and after the ban
reviews <- reviews[reviews$reviewTime>='2016-04-02',]
reviews <- reviews[reviews$reviewTime<='2017-04-02',]
```

```{r, eval = FALSE, include=FALSE}
reviews$date <- as.Date(reviews$reviewTime, "%Y-%m-%d")
reviews$week <- floor_date(reviews$date, "week")
reviews$after_ban <- ifelse(reviews$date>'2016-10-02',1,0)
```


# Data Processing

- Drop records with no product category
```{r, eval = FALSE, include=FALSE}
# Get selected columns for further analysis.
reviews.product <- reviews[,c('overall', 'vote', 'verified', 'reviewerID', 'asin', 'word_count', 'image', 'category', 'brand', 'price', 'main_cat', 'amazon', 'sim1', 'date', 'week', 'after_ban')]
reviews.product$rating <- reviews.product$overall
reviews.product$item_id <- reviews.product$asin
reviews.product$helpful_yes <- reviews.product$vote
reviews.product$image_count <- reviews.product$image
```

```{r, eval = FALSE, include=FALSE}
did.reviews <- reviews.product[,c('rating', 'helpful_yes', 'verified', 'reviewerID', 'item_id', 'word_count', 'image_count', 'category', 'brand', 'price', 'main_cat', 'amazon', 'sim1', 'date', 'week', 'after_ban')]
```

```{r, eval = FALSE, include=FALSE}
# List of dependent variables
# Compute weekly stats for each product
# Mean measurement by week
did.reviews <- reviews %>%
  group_by(asin, week) %>%
  mutate(weekly_review_count = n()) %>%
  mutate(avg_rating = mean(overall)) %>%
  mutate(avg_sentiment = mean(sentiment)) %>%
  mutate(avg_word_count = mean(word_count)) %>%
  mutate(avg_vote = mean(vote)) %>%
  mutate(avg_image = mean(image))
```

```{r eval = FALSE, include=FALSE}
did.reviews <- did.reviews %>%
  group_by(item_id, week) %>%
  mutate(week_n_incentivized = sum(incentivized)) %>%
  mutate(week_n_verified = sum(verified_purchaser)) %>%
  mutate(week_incentivized = week_n_incentivized / week_n) %>%
  mutate(week_verified = week_n_verified / week_n)
```

```{r, include=FALSE}
# Write to save
write.csv(did.reviews, file="~/Dropbox/Eugenie/data/processed_julian_amazon_data/did/reviews_mcauley_description_full.csv", row.names=FALSE)
```

```{r, results='asis', echo=FALSE}
# eval = FALSE, 
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ word_count * image_count, index = c('category'), model = 'within')

stargazer(fe.helpful_yes, title="Linear Regression FE on Product Category Results", align=TRUE, type='html', dep.var.labels=c("Helpfulness"), covariate.labels=c("Length","Image count"))
```

```{r, eval = FALSE, results='asis', echo=FALSE}
fe.rating <- plm(data = did.reviews, formula = rating ~ incentivized, index = c('category'), model = 'within')
fe.positive <- plm(data = did.reviews, formula = positive ~ incentivized, index = c('category'), model = 'within')
fe.word_count <- plm(data = did.reviews, formula = word_count ~ incentivized, index = c('category'), model = 'within')
fe.image <- plm(data = did.reviews, formula = image_count ~ incentivized, index = c('category'), model = 'within')
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ incentivized, index = c('category'), model = 'within')

stargazer(fe.rating, fe.positive, fe.word_count, fe.helpful_yes, fe.image, title="Linear Regression FE on Product Category Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness","Image count"), covariate.labels=c("Incentivized"))
```

```{r, eval = FALSE, results='asis', echo=FALSE}
fe.rating <- plm(data = did.reviews, formula = rating ~ incentivized, index = c('brand'), model = 'within')
fe.positive <- plm(data = did.reviews, formula = positive ~ incentivized, index = c('brand'), model = 'within')
fe.word_count <- plm(data = did.reviews, formula = word_count ~ incentivized, index = c('brand'), model = 'within')
fe.image <- plm(data = did.reviews, formula = image_count ~ incentivized, index = c('brand'), model = 'within')
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ incentivized, index = c('brand'), model = 'within')

stargazer(fe.rating, fe.positive, fe.word_count, fe.helpful_yes, fe.image, title="Linear Regression FE on Brand Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness","Image count"), covariate.labels=c("Incentivized"))
```

```{r, eval = FALSE, results='asis', echo=FALSE}
fe.rating <- plm(data = did.reviews, formula = rating ~ incentivized, index = c('item_id'), model = 'within')
fe.positive <- plm(data = did.reviews, formula = positive ~ incentivized, index = c('item_id'), model = 'within')
fe.word_count <- plm(data = did.reviews, formula = word_count ~ incentivized, index = c('item_id'), model = 'within')
fe.image <- plm(data = did.reviews, formula = image_count ~ incentivized, index = c('item_id'), model = 'within')
fe.helpful_yes <- plm(data = did.reviews, formula = helpful_yes ~ incentivized, index = c('item_id'), model = 'within')

stargazer(fe.rating, fe.positive, fe.word_count, fe.helpful_yes, fe.image, title="Linear Regression FE on Product Results", align=TRUE, type='html', dep.var.labels=c("Rating","Sentiment","Length","Helpfulness","Image count"), covariate.labels=c("Incentivized"))
```


# Get products
```{r, include=FALSE}
did.products <- did.reviews[,c('item_id','category','weekly_review_count','avg_rating','avg_word_count','avg_vote','avg_image','week','after_ban','brand', 'amazon','price','sim1','main_cat')]
did.products <- did.products %>% distinct()
```

```{r, include=FALSE}
# Add amazon attribute
did.products['non_amazon'] <- ifelse(did.products$amazon == 1, 0, 1)
```

```{r, include=FALSE}
# Write to save
write.csv(did.products, file="~/Dropbox/Eugenie/data/processed_julian_amazon_data/did/products_mcauley_description_full.csv", row.names=FALSE)
```

```{r, include=FALSE}
# Split to Amazon and non-Non-Amazon products
did.amazon <- did.products[did.products$non_amazon == 0,]
did.nonamazon <- did.products[did.products$non_amazon == 1,]
```

```{r}
library(knitr)
library(kableExtra)
table <- did.products %>% 
  group_by(category) %>% 
  summarize(brand_count = n_distinct(brand),
            product_count = n_distinct(item_id))
names(table) <- c('Product Category','Brand Count','Product Count')
table %>%
  kable() %>%
  kable_styling()
```

# Diff-in-diff Estimator

```{r, results='asis', echo=FALSE}
# Estimating the DID estimator
didreg.rating = lm(week_rating ~ non_amazon_product * after_ban, data = did.products)
#didreg.sentiment = lm(week_positive ~ non_amazon_product * after_ban, data = did.products)
didreg.length = lm(week_word_count ~ non_amazon_product * after_ban, data = did.products)
didreg.helpfulness = lm(week_helpful_yes ~ non_amazon_product * after_ban, data = did.products)
didreg.image = lm(week_image_count ~ non_amazon_product * after_ban, data = did.products)

stargazer(didreg.rating, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference Results", align=TRUE, type='html', dep.var.labels=c("Rating","Length","Helpfulness", "Image count"),covariate.labels=c("Non-Amazon product","After ban","Non-Amazon product x After ban","Constant"))
```

```{r, results='asis', echo=FALSE}
# Estimating the DID estimator
pdf <- pdata.frame(did.products, index = c("category"))
didreg.rating = plm(week_rating ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
#didreg.sentiment = plm(week_positive ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.length = plm(week_word_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.helpfulness = plm(week_helpful_yes ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.image = plm(week_image_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")

stargazer(didreg.rating, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference with FE on Product Category Results", align=TRUE, type='html', dep.var.labels=c("Rating","Length","Helpfulness", "Image count"),covariate.labels=c("Non-Amazon product","After ban","Non-Amazon product x After ban","Constant"))
```

```{r results='asis', echo=FALSE}
# {r eval = FALSE, results='asis', echo=FALSE}
# Estimating the DID estimator
pdf <- pdata.frame(did.products, index = c("brand"))
didreg.rating = plm(week_rating ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
#didreg.sentiment = plm(week_positive ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.length = plm(week_word_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.helpfulness = plm(week_helpful_yes ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.image = plm(week_image_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")

stargazer(didreg.rating, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference with FE on Brand Results", align=TRUE, type='html', dep.var.labels=c("Rating","Length","Helpfulness", "Image count"),covariate.labels=c("After ban","Non-Amazon product x After ban"))
```


```{r eval = FALSE, results='asis', echo=FALSE}
# {r eval = FALSE, results='asis', echo=FALSE}
# Estimating the DID estimator
pdf <- pdata.frame(did.products, index = c("item_id"))
didreg.rating = plm(week_rating ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
#didreg.sentiment = plm(week_positive ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.length = plm(week_word_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.helpfulness = plm(week_helpful_yes ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")
didreg.image = plm(week_image_count ~ non_amazon_product * after_ban, data = pdf, model = "within", effect = "twoways")

stargazer(didreg.rating, didreg.length, didreg.helpfulness, didreg.image, title="Difference-in-Difference with FE on Product Results", align=TRUE, type='html', dep.var.labels=c("Rating","Length","Helpfulness", "Image count"),covariate.labels=c("After ban","Non-Amazon product x After ban"))
```

# Testing the Assumptions

```{r, results='asis', echo=FALSE}
did.before <- did.products[did.products$after_ban == 0,]
did.before$week <- as.factor(did.before$week)
didreg.rating.before <- lm(week_rating ~ non_amazon_product * week, data = did.before)
#didreg.sentiment.before <- lm(week_positive ~ non_amazon_product * week, data = did.before)
didreg.length.before <- lm(week_word_count ~ non_amazon_product * week, data = did.before)
didreg.helpfulness.before <- lm(week_helpful_yes ~ non_amazon_product * week, data = did.before)
didreg.image.before <- lm(week_image_count ~ non_amazon_product * week, data = did.before)

stargazer(didreg.rating.before, didreg.length.before, didreg.helpfulness.before, didreg.image.before, title="Difference-in-Difference Pre-Treatment Parallel Assumption Check", align=TRUE, type='html', dep.var.labels=c("Rating","Length","Helpfulness", "Image count"))
```

```{r, results='asis', echo=FALSE}
did.before <- did.products[did.products$after_ban == 1,]
did.before$week <- as.factor(did.before$week)
didreg.rating.before <- lm(week_rating ~ non_amazon_product * week, data = did.before)
#didreg.sentiment.before <- lm(week_positive ~ non_amazon_product * week, data = did.before)
didreg.length.before <- lm(week_word_count ~ non_amazon_product * week, data = did.before)
didreg.helpfulness.before <- lm(week_helpful_yes ~ non_amazon_product * week, data = did.before)
didreg.image.before <- lm(week_image_count ~ non_amazon_product * week, data = did.before)

stargazer(didreg.rating.before, didreg.length.before, didreg.helpfulness.before, didreg.image.before, title="Difference-in-Difference Post-Treatment Check", align=TRUE, type='html', dep.var.labels=c("Rating","Length","Helpfulness", "Image count"))
```

