---
title: "Amazon Fire Product Categories & Review Date/Time Part 1"
author: "Eugenie"
date: "30/10/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Data pre-processing is included, where special chars and minimal stop-words are removed.
```{r echo=T, results='hide', message=F, warning=F}
library(data.table)
## load review data
source("~/Dropbox/Eugenie/scripts/libs.R")
```

```{r, include=FALSE}
# Load review data
reviews3.csv <- read.csv("~/Dropbox/Eugenie/data/processed/merged-reviews.csv")
reviews3.csv$date <- as.Date(reviews3.csv$date, "%Y-%m-%d")
reviews3.csv$week <- as.Date(reviews3.csv$week, "%Y-%m-%d")
# Load brand.bi data
tablet_brands <- read_excel("~/Dropbox/Eugenie/data/raw/amazon-tablets.xlsx")
```

```{r, include=FALSE}
# Data Processing
# Drop records before 2013.
reviews3.csv <- reviews3.csv[as.numeric(as.character(reviews3.csv$year))>2013,]
# Drop records with no product category.
reviews3.csv <- reviews3.csv[reviews3.csv$product_cat != 'none',]
# Get selected columns for further analysis.
reviews.product <- reviews3.csv[,c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week')]
```

```{r, include=FALSE}
# Add 'after_ban' label
reviews.product['after_ban'] <- ifelse(reviews.product$date>'2016-10-02',1,0)
reviews.product$after_ban <- as.factor(reviews.product$after_ban)
levels(reviews.product$after_ban) <- c("before", "after")
```

```{r, include=FALSE}
# Get tablets
tablets <- reviews.product[reviews.product$product_cat == "tablets",]
# Get brands
tablets <- merge(tablets, tablet_brands)
# Fire ids
fire.id <- c("B010BWYDYA", "B01GEW27DA", "B01M3ULMWP", "B01MTF2Z37", "B073VVC94R", "B077H3HJJM", "B07F4P3JH7", "B0794Z55CH", "B07N8VFFNS", "B07N8XHDVX", "B0794PD8NR")
# Get binary brands
tablets["brand.bi"] <- ifelse(tablets$item_id %in% fire.id, "fire", "other")
```

```{r,include=FALSE}
# Compute rating stats without splitting incentivized vs. non-incentivized reviews at all
reviews.product <- tablets

# Mean rating by day
reviews.product <- reviews.product %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

# Mean rating by week
reviews.product <- reviews.product %>%
  group_by(brand.bi, year, week) %>%
  mutate(week_rating = mean(rating))
```

# Time Data vs. Rating
## Data processing
Split data on date without splitting incentivized vs. non-incentivized reviews after 2016-10-03.
```{r}
## split on date
reviews.product_non <- reviews.product[reviews.product$date<'2016-10-03'&reviews.product$incentivized=='non-incentivized',]
reviews.product_incentivized <- reviews.product[reviews.product$date<'2016-10-03'&reviews.product$incentivized=='incentivized',]
reviews.product_after <- reviews.product[reviews.product$date>'2016-10-03',]
```

Split data on date with split incentivized vs. non-incentivized reviews after 2016-10-03.
```{r}
## split on date
reviews.product_non1 <- reviews.product[reviews.product$date<'2016-10-03'&reviews.product$incentivized=='non-incentivized',]
reviews.product_incentivized1 <- reviews.product[reviews.product$date<'2016-10-03'&reviews.product$incentivized=='incentivized',]
reviews.product_non2 <- reviews.product[reviews.product$date>'2016-10-03'&reviews.product$incentivized=='non-incentivized',]
reviews.product_incentivized2 <- reviews.product[reviews.product$date>'2016-10-03'&reviews.product$incentivized=='incentivized',]
```

Compute rating stats without splitting incentivized vs. non-incentivized reviews after 2016-10-03.
```{r}
## mean rating by day
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

## mean rating by week
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_rating = mean(rating))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_rating = mean(rating))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_rating = mean(rating))

## mean rating by month
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, month) %>%
  mutate(month_rating = mean(rating))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, month) %>%
  mutate(month_rating = mean(rating))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, month) %>%
  mutate(month_rating = mean(rating))
```

Compute rating stats with split incentivized vs. non-incentivized reviews after 2016-10-03, using the same procedure as above.
```{r,include=FALSE}
## mean rating by day
reviews.product_non1 <- reviews.product_non1 %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

reviews.product_incentivized1 <- reviews.product_incentivized1 %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

reviews.product_non2 <- reviews.product_non2 %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

reviews.product_incentivized2 <- reviews.product_incentivized2 %>%
  group_by(brand.bi, date) %>%
  mutate(day_rating = mean(rating))

## mean rating by week
reviews.product_non1 <- reviews.product_non1 %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_rating = mean(rating))

reviews.product_incentivized1 <- reviews.product_incentivized1 %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_rating = mean(rating))

reviews.product_non2 <- reviews.product_non2 %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_rating = mean(rating))

reviews.product_incentivized2 <- reviews.product_incentivized2 %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_rating = mean(rating))

## mean rating by month
reviews.product_non1 <- reviews.product_non1 %>%
  group_by(brand.bi, month) %>%
  mutate(month_rating = mean(rating))

reviews.product_incentivized1 <- reviews.product_incentivized1 %>%
  group_by(brand.bi, month) %>%
  mutate(month_rating = mean(rating))

reviews.product_non2 <- reviews.product_non2 %>%
  group_by(brand.bi, month) %>%
  mutate(month_rating = mean(rating))

reviews.product_incentivized2 <- reviews.product_incentivized2 %>%
  group_by(brand.bi, month) %>%
  mutate(month_rating = mean(rating))
```


## Plot mean rating over time by brand.bi without splitting incentivized vs. non-incentivized reviews after 2016-10-03

Although there're still reviews labelled as incentivized after 2016-10-03, since I'm not sure how that happened (e.g., prediction from ReviewMeta), I'm leaving it unsplit. The split version of the same analysis is in the next section.

### Rating average by day
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_rating))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.3,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')
```

Observed that prior to 2016-10-03, the day average of incentivized reviews is generally higher and has a greater variation than non-incentivized reviews.

### Rating averaged by week
```{r,echo=FALSE}
## by week
ggplot(NULL, aes(x = week, y = week_rating))+ 
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

### Rating averaged by month
```{r,echo=FALSE}
## by month
ggplot(NULL, aes(x = month, y = month_rating, color = brand.bi))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 0.5,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-02'), color = "black", size=0.3)+
  labs(x='month',y='mean rating',fill='category',title='Product Category Mean Rating by Month')

```

## Plot mean rating over time by brand.bi with split incentivized vs. non-incentivized reviews after 2016-10-03

### Rating average by day
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = date, y = day_rating))+
  geom_point(data=reviews.product_incentivized1, aes(color = "incentivized-before"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non1, aes(color = "non-incentivized-before"), alpha = 0.3,size=0.2)+
  geom_point(data=reviews.product_incentivized2, aes(color = "incentivized-after"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non2, aes(color = "non-incentivized-after"), alpha = 0.3,size=0.2)+
  geom_smooth(data=reviews.product_incentivized1,method = 'auto',aes(color='incentivized-before-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non1,method = 'auto',aes(color='non-incentivized-before-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_incentivized2,method = 'auto',aes(color='incentivized-after-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non2,method = 'auto',aes(color='non-incentivized-after-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')

```

Noticed that due to the lack of data points (i.e., labelled incentivized reviews) after 2016-10-03, the lines are looking weird. I'm not sure if the result is meanful or not, so I'm dropping these for the analysis of word_count and helpful_yes.

Also, the distribution of the labelled incentivized reviews after 2016-10-03 is drastically different than the distribution of the incentivized review before 2016-10-03 for all three known product categories. How the 'incentivized' reviews got labelled is questionable.

### Rating averaged by week
```{r,echo=FALSE}
## by week
ggplot(NULL, aes(x = week, y = week_rating))+ 
  geom_point(data=reviews.product_incentivized1, aes(color = "incentivized-before"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non1, aes(color = "non-incentivized-before"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_incentivized2, aes(color = "incentivized-after"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non2, aes(color = "non-incentivized-after"), alpha = 0.5,size=0.2)+
  geom_smooth(data=reviews.product_incentivized1,method = 'auto',aes(color='incentivized-before-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non1,method = 'auto',aes(color='non-incentivized-before-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_incentivized2,method = 'auto',aes(color='incentivized-after-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non2,method = 'auto',aes(color='non-incentivized-after-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

### Rating averaged by month
Basically the same graph as the 'rating average by week'.


# Word Count
## Data Processing
Compute word count stats with the same precudure as above.
```{r,include=FALSE}
## mean word_count by day
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, date) %>%
  mutate(day_word.count = mean(word_count))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, date) %>%
  mutate(day_word.count = mean(word_count))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, date) %>%
  mutate(day_word.count = mean(word_count))

## mean word_count by week
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_word.count = mean(word_count))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_word.count = mean(word_count))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, date) %>%
  mutate(week_word.count = mean(word_count))

## mean word_count by month
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, month) %>%
  mutate(month_word.count = mean(word_count))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, month) %>%
  mutate(month_word.count = mean(word_count))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, date) %>%
  mutate(month_word.count = mean(word_count))
```


## Plot mean word_count over time by brand.bi
### word_count average by day
```{r,echo=FALSE}
## plot by date
## geom_smooth() using method = 'gam' and formula y ~ s(x, bs = "cs")
ggplot(NULL, aes(x = date, y = day_word.count))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 1,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean word_count',fill='category',title='Product Category Mean word_count by Day')
```

Same as the rating analysis, observed that prior to 2016-10-03, the daily word count average of incentivized reviews is higher and has a greater variation than non-incentivized reviews.

### word_count averaged by week
```{r,echo=FALSE}
## geom_smooth() using method = 'gam' and formula y ~ s(x, bs = "cs")
ggplot(NULL, aes(x = week, y = week_word.count))+ 
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 1,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean word_count',fill='category',title='Product Category Mean word_count by Week')
```

On a weekly scale, the average and variation of the word count of the incentivized reviews prior to 2016-10-03 is still high, but the range of the outliers got tuned down a bit.

### word_count averaged by month
```{r,echo=FALSE}
## by month
## geom_smooth() using method = 'gam' and formula y ~ s(x, bs = "cs")
ggplot(NULL, aes(x = month, y = month_word.count, color = brand.bi))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 1,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-02'), color = "black", size=0.3)+
  labs(x='month',y='mean word_count',fill='category',title='Product Category Mean word_count by Month')
```



# Helpful_yes
## Data Processing
Compute helpful_yes stats with the same precudure as above.
```{r,include=FALSE}
## mean helpful_yes by day
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, date) %>%
  mutate(day_helpful.yes = mean(helpful_yes))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, date) %>%
  mutate(day_helpful.yes = mean(helpful_yes))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, date) %>%
  mutate(day_helpful.yes = mean(helpful_yes))

## mean helpful_yes by week
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_helpful.yes = mean(helpful_yes))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, year, week(date)) %>%
  mutate(week_helpful.yes = mean(helpful_yes))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, date) %>%
  mutate(week_helpful.yes = mean(helpful_yes))

## mean helpful_yes by month
reviews.product_non <- reviews.product_non %>%
  group_by(brand.bi, month) %>%
  mutate(month_helpful.yes = mean(helpful_yes))

reviews.product_incentivized <- reviews.product_incentivized %>%
  group_by(brand.bi, month) %>%
  mutate(month_helpful.yes = mean(helpful_yes))

reviews.product_after <- reviews.product_after %>%
  group_by(brand.bi, date) %>%
  mutate(month_helpful.yes = mean(helpful_yes))
```

## General stats
As we discovered in previous analysis, the helpful_yes factor is very sparse. Also, it's a bit suspicious that we only have 3 reviews with the count of helpful_yes greater than 0 since 2016-10-03. 
```{r}
cat_sum <- reviews.product %>%
  mutate(is_after = ifelse(date > '2016-10-03','after 2016-10-03','before 2016-10-03')) %>%
  mutate(is_zero = ifelse(helpful_yes > 0,'greater than 0','0')) %>%
  group_by(is_after,is_zero) %>%
  summarise(review.count = n()) %>%
  mutate(review.pct = review.count/sum(review.count)*100)
cat_sum
```


## Plot mean helpful_yes over time by brand.bi
### helpful_yes average by day
```{r,echo=FALSE}
## plot by date
## geom_smooth() using method = 'gam' and formula y ~ s(x, bs = "cs")
ggplot(NULL, aes(x = date, y = day_helpful.yes))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 1,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean helpful_yes',fill='category',title='Product Category Mean helpful_yes by Day')
```

### helpful_yes averaged by week
```{r,echo=FALSE}
## geom_smooth() using method = 'gam' and formula y ~ s(x, bs = "cs")
ggplot(NULL, aes(x = week, y = week_helpful.yes))+ 
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 1,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='week',y='mean helpful_yes',fill='category',title='Product Category Mean helpful_yes by Week')
```

### helpful_yes averaged by month
```{r,echo=FALSE}
## by month
## geom_smooth() using method = 'gam' and formula y ~ s(x, bs = "cs")
ggplot(NULL, aes(x = month, y = month_helpful.yes, color = brand.bi))+
  geom_point(data=reviews.product_incentivized, aes(color = "incentivized"), alpha = 1,size=0.2)+
  geom_point(data=reviews.product_non, aes(color = "non-incentivized"), alpha = 0.5,size=0.2)+
  geom_point(data=reviews.product_after, aes(color = "unidentified"), alpha = 1,size=0.2)+
  geom_smooth(data=reviews.product_incentivized,method = 'auto',aes(color='incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_non,method = 'auto',aes(color='non-incentivized-line'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after,method = 'auto',aes(color='unidentified-line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(brand.bi))+
  geom_vline(xintercept = as.Date('2016-10-02'), color = "black", size=0.3)+
  labs(x='month',y='mean helpful_yes',fill='category',title='Product Category Mean helpful_yes by Month')
```

