---
title: "Mcauley dataset time-series"
author: "Eugenie"
date: "06/25/2020"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Load data.
```{r, include=FALSE}
########################## load library ############################
## for data manipulation
library(plyr)
library(dplyr)
library(tidyr)
library(purrr)
library(readr)
library(stringr)
library(reshape)

## for plotting
library(ggplot2)
library(ggmosaic)
library(plotly)
library(ggpubr)

## for modelling
library(plm)
library(mgcv)
library(GoodmanKruskal)

## for sentiment analysis
library(tidytext)
library(textdata)
library(textclean)
library(gutenbergr)
library(scales)
library(tm)
library(sentimentr)

## read .xlsx files
library(readxl)

## time/date
library(chron)
library(lubridate)

## for tables
library(stargazer)
```

```{r}
reviews3.csv <- read.csv("~/Dropbox/Eugenie/data/processed_julian_amazon_data/did/reviews_mcauley_description_top10_extend.csv")
```


# Data Processing
Get selected columns for further analysis.
```{r}
reviews.product <- reviews3.csv

#names(reviews.product) <- c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week','positive','neutral')
```

Drop records before 2012.
```{r}
#reviews2.temp <- reviews2.temp[as.numeric(as.character(reviews2.temp$year))>2013,]
```

Drop records after 2018-10-07 since it's not a full week.
```{r}
## turn factor to date variable
reviews.product$reviewTime <- as.Date(reviews.product$reviewTime, "%Y-%m-%d")
reviews.product <- reviews.product[reviews.product$reviewTime < '2017-04-06',]
```


# Time Data vs. Positive Sentiment Probability
## Data processing

Split data on date without splitting incentivized vs. non-incentivized reviews after 2016-10-03.
```{r,include=FALSE}
## split on date
reviews.product_before_non <- reviews.product[reviews.product$reviewTime<'2016-10-03'&reviews.product$amazon==0,]
reviews.product_before_amazon <- reviews.product[reviews.product$reviewTime<'2016-10-03'&reviews.product$amazon==1,]
reviews.product_after_non <- reviews.product[reviews.product$reviewTime>'2016-10-03'&reviews.product$amazon==0,]
reviews.product_after_amazon <- reviews.product[reviews.product$reviewTime>'2016-10-03'&reviews.product$amazon==1,]
```

```{r,include=FALSE}
reviews.product_non <- reviews.product[reviews.product$amazon==0,]
reviews.product_amazon <- reviews.product[reviews.product$amazon==1,]
```

```{r,include=FALSE}
reviews.x <- reviews.product_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = n())

reviews.y <- reviews.product_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = n())
```

```{r,echo=FALSE}
ggplot(NULL, aes(x = reviewTime, y = day_positive))+
  geom_point(data=reviews.y, aes(color = "amazon"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.x, aes(color = "non-amazon"), alpha = 0.3,size=0.2)+
  geom_smooth(data=reviews.y,method = 'auto',aes(color='amazon'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.x,method = 'auto',aes(color='non-amazon'),size=1,alpha = 0.6)+
  theme_minimal()+
  #facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='Date',y='Daily count',fill='category',title='Product Category Review Count by Date')
```

```{r,include=FALSE}
reviews.x <- reviews.product_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(overall))

reviews.y <- reviews.product_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(overall))
```

```{r,echo=FALSE}
ggplot(NULL, aes(x = reviewTime, y = day_positive))+
  geom_point(data=reviews.y, aes(color = "amazon"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.x, aes(color = "non-amazon"), alpha = 0.3,size=0.2)+
  geom_smooth(data=reviews.y,method = 'auto',aes(color='amazon'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.x,method = 'auto',aes(color='non-amazon'),size=1,alpha = 0.6)+
  theme_minimal()+
  #facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='Date',y='Mean rating',fill='category',title='Product Category Mean Rating by Date')
```

```{r,include=FALSE}
reviews.x <- reviews.product_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(sentiment))

reviews.y <- reviews.product_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(sentiment))
```

```{r,echo=FALSE}
ggplot(NULL, aes(x = reviewTime, y = day_positive))+
  geom_point(data=reviews.y, aes(color = "amazon"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.x, aes(color = "non-amazon"), alpha = 0.3,size=0.2)+
  geom_smooth(data=reviews.y,method = 'auto',aes(color='amazon'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.x,method = 'auto',aes(color='non-amazon'),size=1,alpha = 0.6)+
  theme_minimal()+
  #facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='Date',y='Mean sentiment',fill='category',title='Product Category Mean Sentiment by Date')
```

```{r,include=FALSE}
reviews.x <- reviews.product_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(word_count))

reviews.y <- reviews.product_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(word_count))
```

```{r,echo=FALSE}
ggplot(NULL, aes(x = reviewTime, y = day_positive))+
  geom_point(data=reviews.y, aes(color = "amazon"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.x, aes(color = "non-amazon"), alpha = 0.3,size=0.2)+
  geom_smooth(data=reviews.y,method = 'auto',aes(color='amazon'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.x,method = 'auto',aes(color='non-amazon'),size=1,alpha = 0.6)+
  theme_minimal()+
  #facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='Date',y='Mean word count',fill='category',title='Product Category Mean Word Count by Date')
```

```{r,include=FALSE}
reviews.x <- reviews.product_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(image))

reviews.y <- reviews.product_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(image))
```

```{r,echo=FALSE}
ggplot(NULL, aes(x = reviewTime, y = day_positive))+
  geom_point(data=reviews.y, aes(color = "amazon"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.x, aes(color = "non-amazon"), alpha = 0.3,size=0.2)+
  geom_smooth(data=reviews.y,method = 'auto',aes(color='amazon'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.x,method = 'auto',aes(color='non-amazon'),size=1,alpha = 0.6)+
  theme_minimal()+
  #facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='Date',y='Mean image count',fill='category',title='Product Category Mean Image Count by Date')
```

```{r,include=FALSE}
reviews.x <- reviews.product_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(vote))

reviews.y <- reviews.product_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(vote))
```

```{r,echo=FALSE}
ggplot(NULL, aes(x = reviewTime, y = day_positive))+
  geom_point(data=reviews.y, aes(color = "amazon"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.x, aes(color = "non-amazon"), alpha = 0.3,size=0.2)+
  geom_smooth(data=reviews.y,method = 'auto',aes(color='amazon'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.x,method = 'auto',aes(color='non-amazon'),size=1,alpha = 0.6)+
  theme_minimal()+
  #facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='Date',y='Mean helpfulness count',fill='category',title='Product Category Mean Helpfulness Count by Date')
```


Compute positive sentiment stats without splitting incentivized vs. non-incentivized reviews after 2016-10-03.
```{r,include=FALSE}
## mean positive sentiment probability by day
reviews.product_before_non <- reviews.product_before_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(sentiment))

reviews.product_before_amazon <- reviews.product_before_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(sentiment))

reviews.product_after_non <- reviews.product_after_non %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(sentiment))

reviews.product_after_amazon <- reviews.product_after_amazon %>%
  group_by(reviewTime) %>%
  mutate(day_positive = mean(sentiment))

## mean positive sentiment probability by week
# reviews.product_non <- reviews.product_non %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_positive = mean(positive))
# 
# reviews.product_incentivized <- reviews.product_incentivized %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_positive = mean(positive))
# 
# reviews.product_after <- reviews.product_after %>%
#   group_by(product_cat, year, week(date)) %>%
#   mutate(week_positive = mean(positive))

# ## mean positive sentiment probability by month
# reviews.product_non <- reviews.product_non %>%
#   group_by(product_cat, month) %>%
#   mutate(month_positive = mean(positive))
# 
# reviews.product_incentivized <- reviews.product_incentivized %>%
#   group_by(product_cat, month) %>%
#   mutate(month_positive = mean(positive))
# 
# reviews.product_after <- reviews.product_after %>%
#   group_by(product_cat, month) %>%
#   mutate(month_positive = mean(positive))
```

## Plot mean positive sentiment probability over time by product_cat without splitting incentivized vs. non-incentivized reviews after 2016-10-03

### Positive sentiment probability average by day
```{r,echo=FALSE}
## plot by day
ggplot(NULL, aes(x = reviewTime, y = day_positive))+
  geom_point(data=reviews.product_before_amazon, aes(color = "amazon_before"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.product_before_non, aes(color = "non-amazon_before"), alpha = 0.3,size=0.2)+
  geom_point(data=reviews.product_after_non, aes(color = "non-amazon_after"), alpha = 0.7,size=0.2)+
  geom_point(data=reviews.product_after_amazon, aes(color = "amazon_after"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product_before_amazon,method = 'auto',aes(color='amazon_before'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_before_non,method = 'auto',aes(color='non-amazon_before'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after_non,method = 'auto',aes(color='non-amazon_after'),size=1,alpha = 0.6)+
  geom_smooth(data=reviews.product_after_amazon,method = 'auto',aes(color='amazon_after'),size=1,alpha = 0.6)+
  theme_minimal()+
  #facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='Date',y='Mean sentiment',fill='category',title='Product Category Mean Sentiment by Date')
```
