---
title: "Product Categories & Review Date/Time Part 2"
author: "Eugenie"
date: "06/08/2019"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Source File

Data pre-processing is included, where special chars and minimal stop-words are removed.
```{r echo=T, results='hide', message=F, warning=F}
## load review data
source("~/Dropbox/Eugenie/scripts/utils.R")
```


# Data Processing
Add category data as extra columns. Join on either item_id or child_id.
```{r}
reviews2.temp <- reviews2.csv
```

Drop records before 2012.
```{r}
reviews2.temp <- reviews2.temp[as.numeric(as.character(reviews2.temp$year))>2013,]
```

Drop records after 2018-10-07 since it's not a full week.
```{r}
reviews2.temp <- reviews2.temp[reviews2.temp$date < '2018-10-07',]
```

Drop records with no product category.
```{r}
reviews2.temp <- reviews2.temp[reviews2.temp$product_cat != 'none',]
```

Get selected columns for further analysis.
```{r}
reviews.product <- reviews2.temp[,c('recid','item_id','incentivized','product_cat','rating','word_count','helpful_yes','date','year','month','week')]
```

Compute rating stats without splitting incentivized vs. non-incentivized reviews at all.
```{r,include=FALSE}
## mean rating by day
reviews.product <- reviews.product %>%
  group_by(product_cat, date) %>%
  mutate(day_rating = mean(rating))

## mean rating by week
reviews.product <- reviews.product %>%
  group_by(product_cat, year, week(date)) %>%
  mutate(week_rating = mean(rating))

## mean rating by month
reviews.product <- reviews.product %>%
  group_by(product_cat, month) %>%
  mutate(month_rating = mean(rating))
```

Bin the review length.
```{r,include=FALSE}
bins <- c(-1,50,100,200,500,Inf)
reviews.product['word_count.binned'] <- cut(reviews.product$word_count, 
                                        breaks=bins, labels=c('0-50','50-100','100-200','200-500','500+'))
reviews.product$word_count.binned <- as.factor(reviews.product$word_count.binned)
```


# Time Data vs. Rating

## Plot mean rating over time by product_cat without splitting incentivized vs. non-incentivized reviews at all

### Rating average by day
```{r}
## plot by day
ggplot(NULL, aes(x = date, y = day_rating))+
  geom_point(data=reviews.product, aes(color = "daily ave rating"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='daily ave rating line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Day')
```

### Rating averaged by week
```{r,echo=FALSE}
## plot by week
ggplot(NULL, aes(x = week, y = week_rating))+
  geom_point(data=reviews.product, aes(color = "weekly ave rating"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='weekly ave rating line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Week')
```

### Rating averaged by month
```{r,echo=FALSE}
## plot by month
ggplot(NULL, aes(x = month, y = month_rating))+
  geom_point(data=reviews.product, aes(color = "monthly ave rating"), alpha = 0.7,size=0.2)+
  geom_smooth(data=reviews.product,method = 'auto',aes(color='monthly ave rating line'),size=1,alpha = 0.6)+
  theme_minimal()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  labs(x='day',y='mean rating',fill='category',title='Product Category Mean Rating by Month')
```


## Plot rating distribution by proportion

### Rating proportion in a day
```{r,echo=FALSE}
## percentage of rating vs. week
ggplot(data=reviews.product, aes(date))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

### Rating proportion in a week
```{r,echo=FALSE}
## percentage of rating vs. week
ggplot(data=reviews.product, aes(week))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

### Rating proportion in a month
```{r,echo=FALSE}
## percentage of rating vs. week
ggplot(data=reviews.product, aes(month))+
  geom_bar(aes(fill=as.factor(rating)), position="fill")+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```


## Plot rating distribution by count

### Rating count in a day
```{r,echo=FALSE}
ggplot(reviews.product, aes(date, fill=as.factor(rating)))+
  geom_bar()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")
```

### Rating count in a week
```{r,echo=FALSE}
ggplot(reviews.product, aes(week, fill=as.factor(rating)))+
  geom_bar()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")
```

### Rating count in a month
```{r,echo=FALSE}
ggplot(reviews.product, aes(month, fill=as.factor(rating)))+
  geom_bar()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")
```


# Time Data vs. Review Length

## Plot rating distribution by proportion

### Rating proportion in a day
```{r,echo=FALSE}
ggplot(data=reviews.product, aes(date))+
  geom_bar(aes(fill=word_count.binned), position="fill")+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

### Rating proportion in a week
```{r,echo=FALSE}
## percentage of rating vs. week
ggplot(data=reviews.product, aes(week))+
  geom_bar(aes(fill=word_count.binned), position="fill")+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```

### Rating proportion in a month
```{r,echo=FALSE}
ggplot(data=reviews.product, aes(month))+
  geom_bar(aes(fill=word_count.binned), position="fill")+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")+
  ylab('proportion')
```


## Plot rating distribution by count

### Rating count in a day
```{r,echo=FALSE}
ggplot(reviews.product, aes(date, fill=word_count.binned))+
  geom_bar()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")
```

### Rating count in a week
```{r,echo=FALSE}
ggplot(reviews.product, aes(week, fill=word_count.binned))+
  geom_bar()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")
```

### Rating count in a month
```{r,echo=FALSE}
ggplot(reviews.product, aes(month, fill=word_count.binned))+
  geom_bar()+
  facet_grid(rows=vars(product_cat))+
  geom_vline(xintercept = as.Date('2016-10-03'), color = "black", size=0.3)+
  scale_fill_brewer(palette="RdBu")
```



